---
title: "**V.a.** Community-Psychology-Specific Literature Review"
author: "Rachel M. Smith"
date: "`r format(Sys.Date(), '%d %B %Y')`"
---

```{r setup_Va, echo=FALSE, results='hide', fig.keep='none', fig.show='none', message=FALSE, warning=FALSE, cache=FALSE}
rm(list = ls())
source("bibs_cp.R")
knitr::opts_chunk$set(echo = FALSE)
panderOptions("p.wrap", "")
panderOptions("p.sep", "; ")
panderOptions("p.copula", "; ")
```

\doublespacing

# Critical Methodological Review of Community-Psychology IPV Interventions Research

The previously reviewed literature represents a subset of the foundational IPV perpetrator interventions literature, as the reviewed studies were specifically selected from the larger body of IPV literature based on (a) their general relevance to the substantive research focus of the present review (i.e., IPV interventions), and (b) their alignment with applied community-psychological theory and methods. The remainder of this review, however, will focus specifically on empirical research conducted within disciplines specifically related to community-psychology. Specifically, a methodological critical review of the community-psychology-focused IPV interventions literature is provided in the sections that follow, with a particular focus on the relevance to and implications for IPV intervention and prevention efforts inclusive of sexual minority women [`r paste0("@", MAP$bibkey) %>% pander()`].

## Publication Years

Although the previously-described database searches allowed for any research published between 1965 and the current year (2017), the earliest publication date in the literature reviewed here is `r min(MAP$year)`. This timespan is somewhat aligned with the previously-discussed political and legislative history of U.S. domestic violence policy and social movement(s). For instance, the original Violence Against Women Act (VAWA), which imposed provisions to actually enforce the illegality of family violence perpetration and gave way to more funding allocations for IPV-related research across multiple scientific disciplines, was passed in 1994, [@biden2014twenty; @modi2014role; @fine1998violence; @legates2001their, Ch. 3]. The two-fold implications of the legislative passing of the 1994 VAWA is of particular import to the present review, as the combination of (a) acknowledgement of IPV as a public health issue and (b) widespread government attention and funding being directed toward addressing IPV across multiple levels of analysis and disciplines could provide a nearly ideal landscape for conducting and cultivating innovative community-based action-oriented research.<!--TODO: CITE (esp. CP theoretical citations)-->

## Specific Research Topics

The overarching research topics across the community-psychological empirical literature reviewed here span individual, organizational, community, and structural levels of analysis. Specific topics at the community and structural levels of analysis include (1) development, improvement, and/or evaluations of coordinated community responses to IPV, (2) communities' capacities to address IPV, (3) and public policy related to IPV. Organizational level topics include (1) evaluation of IPV perpetration and/or victimization intervention or prevention programs, (2) evaluation of intervention program policies, and (3) interventions implemented in Non-IPV specific community-based service provider settings (e.g., hospitals). At the individual level, the majority of the reviewed SMW-inclusive research focuses on individual risk factors for IPV victimization and/or perpetration. Additional individual level topics include investigations of perspectives about or perceptions of IPV among individuals with no history of IPV or who are not a part of an intervention's or research investigation's target population, help-seeking behaviors among IPV victims, and consequences of IPV for individual victims or perpetrators. Because this review ultimately seeks to inform IPV intervention and prevention approaches and action-oriented research, details regarding key characteristics and findings among studies focusing on IPV interventions are provided below, followed by an integrative overview of the designs, methodologies, and data collection mechanisms employed across the all of the reviewed community-psychological IPV-related literature.

### IPV Interventions Research

Three of the reviewed studies published in community-psychology-related journals focus on some type of IPV intervention evaluation, two of which [@boal2014impact; @foshee2004assessing] are specific to IPV perpetrator interventions, whereas the remaining intervention-focused investigation [@thompson2000identification] evaluates an IPV victimization-focused intervention. Despite the relatively small number of IPV intervention evaluation studies published in community-psychology-related journals, these investigations collectively cover a range levels of analysis and intervention, settings, and evaluation methods. @thompson2000identification evaluated the efficacy of an intervention implemented in a primary healthcare setting designed to improve healthcare providers' and support staff's identification of IPV among patients and the level and quality of care provided to patients identified as IPV victims. @foshee2004assessing, on the other hand, implemented a multi-site, multi-wave intervention, the _"Safe Dates Project"_, targeting 8^th^-grade (at baseline) adolescents enrolled in ten public schools in North Carolina. The Safe Dates program was designed as a secondary teen dating violence prevention intervention, and comprised a 10-session treatment curriculum, a student-performed theatre production, a treatment booster in the form of an 11-page newsletter mailed to intervention recipients' homes three years after the initial treatment, and a telephone follow-up from a health educator shortly after the booster was mailed. It is somewhat difficult to evaluate the implementation and evaluation of the Safe Dates program using only information provided in @foshee2004assessing\'s relatively brief report. This is troublesome primarily because the treatment booster was found to be associated with _increased_ post-intervention psychological abuse perpetration among adolescents with high baseline psychological abuse scores. Details regarding the content of the booster are not available in the report, most likely due to space restrictions imposed by the publishing journal (_American Journal of Public Health_), which may provide better insight regarding the possible mechanisms by which the treatment booster caused increases in violence perpetration.

Finally, @boal2014impact provide evaluated the implementation of legislative policies guiding IPV perpetrator intervention program practices. This particular investigation mirrors the earlier IPV perpetrator interventions literature published in violence-specific journals reviewed in the previous section in that the authors' evaluation spanned multiple levels of analysis (i.e., structural/policy- and organizational). The overarching research design employed in @boal2014impact\'s longitudinal investigation of the implementation of standards for IPV perpetrator programs reflects a careful examination of the multiple factors influencing these programs' overall and day-to-day practices. However, similar to the earlier perpetrator interventions literature, @boal2014impact's analysis is bound by the limits of the policy and programs under evaluation, as is reflected in the evaluated policy's focus on program practices as they relate to intervention with male-identified individuals who have perpetrated abuse toward female-identified intimate partners.

# VI. Integrative Literature Critique

Research conducted within the subset of community psychology focused around intimate partner violence was initially evaluated according to the level of inclusion and exclusion of the historically marginalized population of particular interest for the purposes of this review: sexual minority women (SMW). The implementation of action-oriented community-psychology methodologies and analytic approaches was then reviewed within each of these categories (i.e., inclusion or exclusion of SMW) in terms of (1) the appropriateness of the methods to the research question(s), (2) how the methods facilitated the inclusion or exclusion of sexual minority women, and (3) whether and how (where applicable) exclusion of sexual minority women is justified.

## Definition of Methodological Rigor

The notion of "scientific rigor" is particularly important in evaluating a set of applied social science research studies employing varying methodologies. This is because "rigor" is not necessarily clearly defined across methodologies, and some research philosophies do not consider certain methodologies as capable of achieving scientific rigor at all. For the purposes of this review, methodological rigor is broadly defined as the extent to which a given study employs research methods that best address the overarching research question(s) and/or hypothesis/hypotheses, and the quality of the implementation of those methods. This definition of methodological rigor therefore does not prioritize a particular method nor category of methods (e.g., quantitative over qualitative, mixed-methods over single-methods, etc.), but rather prioritizes the choice and implementation of methods employed to address a given study's purposes. In addition, this definition of methodological rigor allows for more specific and in-depth consideration of the limitations presented, and not presented, in each study's report.

Rigor in action-oriented community-based research methods was evaluated according to the choice, description, justification, appropriateness, and execution of each reviewed study's design (i.e., experimental or cross-sectional) and overarching methodology (i.e., quantitative, qualitative, or mixed-methods). Each of these aspects of the reviewed literature was identified in terms of each evaluated study's purpose, hypotheses, and/or research questions description, sampling frame definition, sampling and data collection methods, analytic approach(es), and description of findings and limitations. Because the underlying goals of this systematic review are motivated by the continued relative absence of sexual minority women in the larger body of IPV-related empirical research literature, especially in terms of IPV perpetrator interventions research, particular attention was given to the sampling frame definitions and sampling methods employed among the empirical studies reviewed here. That is, the evaluated research included in the present review was specifically evaluated in terms of how the methods facilitate the inclusion or exclusion of specific populations, particularly sexual minority women, and whether and how the exclusion of specific populations is justified in each empirical study's report.

In addition, to assess transparency and reproducibility of the research methods and findings, the overall presentation, dissemination mechanism(s), application, and accessibility of the research was noted where available or applicable. These latter assessments of research transparency and reproducibility also incorporated considerations regarding the incorporation of key and/or distal stakeholders' input. The accessibility of the research to primary and distal stakeholders would be reflected according to whether and how stakeholders are provided information about and access to reports of a given project's progress and findings. The role of stakeholder input in the evaluated community-psychology literature was noted in terms of the extent to which efforts made to ensure that _all available_ stakeholders' and informants' voices are considered throughout the research process, and that certain voices are not unjustifiably privileged over others. These considerations include evaluation of whether feedback is explicitly solicited, or at least accepted when offered, from key stakeholders and informants to the research, and whether such feedback is genuinely considered by the primary researchers of a given investigation.

## Study Designs, Methodologies, & Methods Utilized

The majority of the reviewed studies follow quantitatively-based methodologies ($n = 7; 64\%$), whereas only two of the reviewed community-psychology-specific studies employed qualitative methodological approaches, and another two utilized mixed-methodological approaches. Of the reviewed quantitatively-based studies, $36\%$ ($n = 4$) employed experimental, rather than cross-sectional, designs, of which three followed a longitudinal experimental design (defined for this review as including three or more data collection time-points) and one used a pre-/post-test design (i.e., two data collection time-points). All of the seven quantitatively-based studies used self-report survey measures as the primary datasource. The two qualitatively-based studies collected data using one-on-one interviews. Finally, among the two studies following mixed-methodological designs, one study administered and analyzed data from a self-report survey comprised of open-ended and closed-ended questions ($n = 1$), whereas the second mixed-methods study employed a multi-method approach by collecting data using a combination of closed-ended self-report survey questions, one-on-one interviews, and a focus group.


## Sampling Frame Definitions and Sampling Methods

As previously mentioned, the sampling frame definitions among IPV the reviewed literature specific to IPV perpetrator interventions is almost universally restricted to heterosexual male-identified individuals who have perpetrated IPV. The exception to this overarching trend is @foshee2004assessing\'s randomized control trial evaluation of the Safe Dates program among adolescents, in which the sampling frame was defined according to geography, age, and school type (i.e., 8^th^ grade students enrolled in a selection of public schools located in multiple North Carolina counties).

In general, research related to interventions for which the target population is IPV victims, potential victims, or survivors follows a similar trend, but in the opposing direction, such that the majority of such studies' sampling frames are typically restricted to female-identified individuals who have experienced or who are at risk of experiencing IPV victimization. However, the present review systematically sought out the subset of community-psychology-related IPV research specifically inclusive of sexual minority women. The database searches described earlier in this paper, yielded seven empirical research studies published within community-psychology-related disciplines in which sexual minority women were specifically included in the sampling frame definitions [@blosnich2009comparisons; @balsam2005relationship; @edwards2016college; @glass2008risk; @lewis2014sexual; @oswald2010lesbian; @sylaska2015disclosure], all of which included sexual minority women with histories of IPV victimization. Three of the latter-described studies also included women who had perpetrated IPV toward a same-gender romantic partner [@balsam2005relationship; @glass2008risk; @lewis2014sexual]. The sampling frame definitions for three of the reviewed SMW-inclusive research studies also included sexual minorities identifying as male, transgender, and/or gender-queer [@sylaska2015disclosure; @edwards2016college]. Finally, two studies included heterosexual men and women, in addition to sexual minority women, in their sampling frame definitions [@edwards2016college; @blosnich2009comparisons].

## _A. Strengths_ \todot

## _B. Limitations_ \todot

```{r resetup, echo=FALSE, results='hide', message=FALSE, warning=FALSE, cache=FALSE}
panderOptions("p.wrap", "_")
panderOptions("p.sep", ", ")
panderOptions("p.copula", ", and ")
```

\newpage
