# Appendices

```{r setup, echo=FALSE, results='hide', message=FALSE, warning=FALSE, cache=FALSE, fig.show='none', fig.keep='none'}
source("bibs.R")
knitr::opts_chunk$set(echo=FALSE)
```

```{r dbsrch}
dbsrch <- data.frame(n = c("1.", "2.", "3.", "4.", "5.", "6."),
                     srch = c("Intimate Partner Violence, Domestic Violence, or Partner Abuse - General",
                              "Intimate Partner Violence, Domestic Violence, or Partner Abuse Interventions",
                              "Intimate Partner Violence, Domestic Violence, or Partner Abuse Intervention Evaluations",
                              "Female Same-Sex/Same-Gender Domestic Violence, or Partner Abuse - General",
                              "Female Same-Sex/Same-Gender Domestic Violence, or Partner Abuse Interventions",
                              "Female Same-Sex/Same-Gender Domestic Violence, or Partner Abuse Intervention Evaluations"),
                     nres = c(paste0("$", comma(s1[1]), " - ", comma(s1[2]), "$"),
                              paste0("$", comma(s2[1]), " - ", comma(s2[2]), "$"),
                              paste0("$", comma(s3[1]), " - ", comma(s3[2]), "$"),
                              paste0("$", comma(s4[1]), " - ", comma(s4[2]), "$"),
                              paste0("$", comma(s5[1]), " - ", comma(s5[2]), "$"),
                              paste0("$", comma(s6[1]), " - ", comma(s6[2]), "$"))
                     )

## BELOW IS FOR .TEX/.PDF OUTPUT ##
# dbsrch$srch <- paste0("\\footnotesize{\\textit{", dbsrch$srch, "}}")
# dbsrch$n <- paste0("\\footnotesize{\\textit{", dbsrch$n, "}}")
# dbsrch$nres <- paste0("\\footnotesize{\\textit{", dbsrch$nres, "}}")

## BELOW IS FOR .DOCX OUTPUT ##
dbsrch$srch <- paste0("_", dbsrch$srch, "_")
dbsrch$n <- paste0("_", dbsrch$n, "_")
dbsrch$nres <- paste0("_", dbsrch$nres, "_")

names(dbsrch) <- c("", "Database Search", "$Range_{N_{Results}}$")
kable(dbsrch, caption = "Descriptions of database searches conducted with corresponding ranges of the number of results returned", align = c("r", "l", "c"))

```

\newpage

```{r mapcpv}
map.cpp <- dplyr::rename(map.cp, "Journal" = journal, "Research Category" = scat)

# Rtdf(map.cp$journal, names = c("Publication Title", "$N_{Articles}$")) %>%
with(map.cpp, {ftable(journal, scat)}) %>%
    pander(caption = "\\edit{Community Psychology Journals Included in Literature Search, with Corresponding Number of Reviewed Articles per Journal}")

# Rtdf(map.v$journal, names = c("Publication Title", "$N_{Articles}$")) %>%
    # pander(caption = "\\edit{Violence-Related Journals Included in Literature Search, with Corresponding Number of Reviewed Articles per Journal}")

MAPpr <- dplyr::rename(MAP, "Journal" = journal, "Research Category" = scat)
with(MAPpr, {ftable(journal, scat)}) %>% pander(caption="Number of formally reviewed articles per journal title ")


```

\newpage

```{r mapJrnl}
Rtdf(MAP$journal, names = c("Publication Title", "$N_{Articles}$")) %>%
    pander(caption = "\\edit{Publication Titles of Reviewed Articles}")

with(MAP, {ftable(journal, scat)}) %>% pander(caption="")

```

\newpage


# Appendix C Clinician Rating Form [@gondolf2009clinician]

Date:

Subject Name:

Group Leader (initials): Site:

INSTRUCTIONS: Please rate the man named above on each of the listed criteria. Rate him using the 0 to 5 scale below based on your impressions and observations. Return the form immediately to the evaluation contact person. 5 = extremely present; 4 = very present; 3 = somewhat present; 2 = a little present; 1 = very little present; 0 = no opinion, uncertain, not applicable.

_____ attendance: arrives at group session on time; socializes or lingers afterward; contacts program in advance about absence; has legitimate excuse for absences.
_____ nonviolence: has not recently physically abused partner, children, or others; no apparent threats, intimidation, or manipulation.
_____ sobriety: attends meeting sober; not high or drunk; no apparent abuse of alcohol or drugs during week; complying to ordered or referred drug and alcohol treatment.
_____ acceptance: admits that violence and abuse exists; not minimizing, blaming, or excusing the problem; realizes responsibility for abuse; identifies contribution to problems
_____ using techniques: takes conscious steps to avoid violence; refers to time-outs, self-talk, conflict resolution skills, etc.; does homework assignments or recommendations.
_____ help seeking: seeks information about alternatives; discusses options with others in the group; calls other participants for help; open to referrals and future support.
_____ process conscious: lets others speak one at time; acknowledges others’ contributions; asks questions of others without interrogating; heeds direction of counselors.
_____ actively engaged: attentive body language and nonverbal response; maintains eye contact; speaks with feeling; follows topic of discussion in comments.
_____ self-disclosure: reveals struggles, feelings, fears, and self-doubts; not withholding or evading issues; not sarcastic or defensive.
_____ sensitive language: respectful of partner and women in general; nonsexist language and no pejorative slang; checks others who use sexist language.


# References
