---
title: "Completed \\& In-Progress Graduate Coursework"
author: "Rachel M. Smith"
date: "`r format(Sys.Date(), '%d %B %Y')`"
---

```{r setup, echo=FALSE, results='hide', message = FALSE, warning=FALSE, cache=FALSE}
source("SETUP.R")
knitr::opts_chunk$set(tidy = TRUE, echo = FALSE, cache = FALSE, fig.show = 'hold', results = 'asis', Rplot = TRUE, fig.path = "graphics/rplot_", dev = 'pdf', dpi = 300)
```


# Major,  Minor,  \& Core Program Requirements

`r margin_note("\\textit{Note: '\\textsuperscript{*}' denotes courses applicable to both the major and minor areas.}")`

```{r}
maj <-
    data.frame(
        CRN = c("`PSY 610`", 
                "`PSY 614`", 
                "`PSY 610`", 
                "`PSY 597`", 
                "`PSY 510`"),
        Title = c("_Top: Community \\& Social Interventions_",
                  "_Advanced Applied Social Psychology \\& 
                  Community Psychology_",
                  "_Top: Program Evaluation^`*`^_",
                  "_Applied Survey Research^`*`^_",
                  "_Top: Place-Based Research^`*`^_"), 
        Grade = c("**B+**", 
                  "**A**", 
                  "**A**", 
                  "**A-**", 
                  "**A**"), 
        Hrs = rep(4, 5))
    
kable(maj, caption = "**Major Area Coursework**: Applied 
      Social \\& Community Psychology", 
      col.names = c("CRN", 
                    "Title", 
                    "Grade", 
                    "Credit Hours"),
      align = c('c', 'l', 'c', 'c'))
```

```{r}
minr <-
    data.frame(
        CRN = c("`SOC 610`", 
                "`PSY 610`", 
                "`SOC 610`", 
                "`PSY 510`", 
                "`SOC 610`", 
                "`PSY 597`", 
                "`PSY 510`"),
        Title = c("_Focus Groups_",
                  "_Program Evaluation^`*`^_",
                  "_Qualitative Data Analysis_",
                  "_HLM/Mixed Effects Models for Longitudinal 
                  Data Analysis_",
                  "_Mixed Methods Research_",
                  "_Applied Survey Research^`*`^_",
                  "_Place-Based Research^`*`^_",
                  "__"), 
        Grade = c("**A**",
                  "**A**",
                  "**A**",
                  "**A**",
                  "**A**",
                  "**A-**",
                  "**A**"), 
        Hrs = rep(4, 7))
    
kable(minr, caption = "**Minor Area Coursework**: 
      Mixed Methods Research", 
      col.names = c("CRN", 
                    "Title", 
                    "Grade", 
                    "Credit Hours"),
      align = c('c', 'l', 'c', 'c'))
```

```{r}
reqr <-
    data.frame(
        CRN = c("`PSY 621`",
                "`PSY 618`",
                "`PSY 622`",
                "`PSY 624`"),
        Title = c("_Univariate Quantitative Methods_",
                  "_Ethics \\& Professional Issues in Applied Research 
                  and Practice_",
                  "_Multiple Regression \\& Multivariate 
                  Quantitative Methods_",
                  "_Research Design in Applied Psychology_"), 
        Grade = c("**A-*",
                  "**A**",
                  "**B+*",
                  "**A**"), 
        Hrs = c(5,
                4,
                5,
                4))

kable(reqr, caption = "Research Methods \\& Statistics Coursework 
      Required by Program", 
      col.names = c("CRN", 
                    "Title", 
                    "Grade", 
                    "Credit Hours"),
      align = c('c', 'l', 'c', 'c'))
```
```{r}
prac <-
    data.frame(
        CRN = c("`PSY 609`",
                "`PSY 609`",
                "`PSY 501`"),
        Title = c("_Prac: Violence Prevention I_",
                  "_Prac: Violence Prevention II_",
                  "_Res: BIP Staff Interviews_"), 
        Grade = c("**P**",
                  "**P**",
                  "**A**"), 
        Hrs = c(1,
                1,
                6))

kable(prac, caption = "Research \\& Field-Based Practica", 
      col.names = c("CRN", 
                    "Title", 
                    "Grade", 
                    "Credit Hours"),
      align = c('c', 'l', 'c', 'c'))
```

Table: Credit Hours and GPA in Major and Minor Areas (for completed courses)

| $N_{courses}$ | GPA Hours | GPA
| :--------- | :-------- | :----
| **Major**
| 5 (2 Major-Only) | 20.000 | 3.80
| **Minor:**
| 8 (4 Minor-Only) | 32.000 | 3.96
| **Combined Major \& Minor**
| 9 | 36.000 | 3.88
| **Combined Major, Minor, \& Methods/Statistics Requirements**
| 12 | 50 | 3.85



\newpage

# Full Transcript for All Graduate Coursework


Table: All Completed and In-Progress Courses

| `CRN`      | _Title_  | **Grade** | Credit Hours
| :--------- | :----- | :---- | :------------|
| `R Tufte::Newthought("Fall 2013 Quarter")` | | |
| `PSY 609` | _Prac: Violence Prevention I_ | **P** | 1
| `PSY 610` | _Top: Community \& Social Interventions_ | **B+** | 4
| `PSY 621` | _Univariate Quantitative Methods_ | **A-** | 5
| `R Tufte::Newthought("Winter 2014 Quarter")` | | |
| `PSY 609` | _Prac: Violence Prevention II_ | **P** | 1
| `PSY 618` | _Ethics \& Prof Iss App Rsrch/Pr_ | **A** | 4
| `PSY 622` | _Multiple Regression \& Multivariate Quantitative Methods_ | **B+** | 5
| `R Tufte::Newthought("Spring 2014 Quarter")` | | |
| `PSY 614` | _Advanced Applied Social Psychology \& Community Psychology_ | **A** | 4
| `PSY 624` | _Research Design in Applied Psychology_ | **A** | 4
| `SOC 610` | _Top: Focus Groups_ | **A** | 4
| `R Tufte::Newthought("Summer 2014 Quarter")` | | |
| `PSY 503` | _Thesis_ | `Ip` | 5
| `R Tufte::Newthought("Fall 2014 Quarter")` | | |
| `PSY 503` | _Thesis_ | `Ip` | 1
| `PSY 610` | _Top: Program Evaluation_ | **A** | 4
| `SOC 610` | _Top: Qualitative Data Analysis_ | **A** | 4
| `R Tufte::Newthought("Winter 2015 Quarter")` | | |
| `PSY 510` | _Top: HLM/Mixed Effects Models for Longitudinal Data Analysis_ | **A** | 4
| `PSY 615` | _Advanced Applied Developmental Psychology_ | **A** | 4
| `SOC 610` | _Top: Mixed Methods Research_ | **A** | 4
| `R Tufte::Newthought("Spring 2015 Quarter")` | | |
| `PSY 501` | _Res: BIP Staff Interviews_ | **A** | 2
| `PSY 503` | _Thesis_ | `Ip` | 3
| `PSY 597` | _Applied Survey Research_ | **A-** | 4
| `R Tufte::Newthought("Fall 2015 Quarter")` | | |
| `PSY 501` | _Res: BIP Staff Interview_ | **A** | 3
| `PSY 503` | _Thesis_ | `Ip` | 2
| `PSY 516` | _Advanced Organizational Psychology_ | **A-** | 4
| `R Tufte::Newthought("Winter 2016 Quarter")` | | |
| `PSY 503` | _Thesis_ | `Ip` | 4
| `PSY 510` | _Top: Place-Based Research_ | **A** | 4
| `PSY 601` | _Res: BIP Staff Interview_ | **A** | 1
| `R Tufte::Newthought("_Term: Spring 2016 Quarter `(In Progress")`_)` | | |
| `PSY 610` | _Top: Introduction to Psychological Measure_ | **C** | 4
| `R Tufte::Newthought("_Term: Fall 2016 Quarter `(In Progress")`_)` | | |
| `PSY 610` | _Top: Categorical Data Analysis_ | `Na` | 4


Table: Credit Hours and GPA

| GPA Hours | Quality Points | GPA
| :-------- | :------------- | :----
| `r tufte::newthought("Fall 2013 Quarter")`
| 9 | 31.67 | 3.51
| _PSU Cumulative:_
| 9 | 31.67 | 3.51
| `r tufte::newthought("Winter 2014 Quarter")`
| 9 | 32.65 | 3.62 |
| _PSU Cumulative:_
| 18 | 64.32 | 3.57 |
| `r tufte::newthought("Spring 2014 Quarter")`
| 12 | 48.00 | 4.00
| _PSU Cumulative:_
| 30 | 112.32 | 3.74
| `r tufte::newthought("Fall 2014 Quarter")`
| 8 | 32.00 | 4.00
| _PSU Cumulative:_
| 38 | 144.32 | 3.79
| `r tufte::newthought("Winter 2015 Quarter")`
| 12 | 48.00 | 4.00
| _PSU Cumulative:_
| 50 | 192.32 | 3.84
| `r tufte::newthought("Spring 2015 Quarter")`
| 6 | 22.68 | 3.78
| _PSU Cumulative:_
| 56 | 215.00 | 3.83
| `r tufte::newthought("Fall 2015 Quarter")`
| 7 | 26.68 | 3.81
| _PSU Cumulative:_
| 63 | 241.68 | 3.83
| `r tufte::newthought("Winter 2016 Quarter")`
| 5 | 20.00 | 4.00
| _PSU Cumulative:_
| 68 | 261.68 | 3.84
| `r tufte::newthought("\\large{Total Institution:}")`
| 68 | 261.68 | 3.84
