---
title: "Comprehensive Examination Proposal"
author: "Rachel M. Smith"
date: "`r format(Sys.Date(), '%d %B %Y')`"
---

```{r setup, echo=FALSE, results='hide', message=FALSE, warning=FALSE, cache=FALSE}
source("SETUP.R")
knitr::opts_chunk$set(
    tidy = FALSE,
    echo = FALSE,
    cache = FALSE,
    fig.keep = 'high',
    fig.show = 'hold',
    results = 'asis',
    autodep = TRUE,
    Rplot = TRUE,
    fig.path = 'graphics/rplot-',
    fig.width = 7,
    fig.height = 7,
    out.width = "\\linewidth"
    )
```

# (A) Completed Foundational Coursework \complete

_**Note:** '^`*`^' denotes courses applicable to both the major and minor areas._

```{r maj}
maj <-
    data.frame(
        CRN = c("`PSY 610`",
                "`PSY 614`",
                "`PSY 610`",
                "`PSY 597`",
                "`PSY 510`"),
        Title = c("_Top: Community & Social Interventions_",
                  "_Advanced Applied Social Psychology & Community Psychology_",
                  "_Top: Program Evaluation^`*`^_",
                  "_Applied Survey Research^`*`^_",
                  "_Top: Place-Based Research^`*`^_"),
        Grade = c("B+",
                  "A",
                  "A",
                  "A-",
                  "A"),
        Hrs = rep(4, 5))

knitr::kable(maj, caption = "**Major Area Coursework**: Applied
      Social & Community Psychology",
      col.names = c("CRN",
                    "Title",
                    "Grade",
                    "Credit Hours"),
      align = c('c', 'l', 'c', 'c'))
```

```{r, minr}
minr <-
    data.frame(
        CRN = c("`SOC 610`",
                "`PSY 610`",
                "`SOC 610`",
                "`PSY 510`",
                "`SOC 610`",
                "`PSY 597`",
                "`PSY 510`"),
        Title = c("_Focus Groups_",
                  "_Program Evaluation^`*`^_",
                  "_Qualitative Data Analysis_",
                  "_HLM/Mixed Effects Models for Longitudinal Data Analysis_",
                  "_Mixed Methods Research_",
                  "_Applied Survey Research^`*`^_",
                  "_Place-Based Research^`*`^_"),
        Grade = c("A",
                  "A",
                  "A",
                  "A",
                  "A",
                  "A-",
                  "A"),
        Hrs = rep(4, 7))

knitr::kable(minr, caption = "**Minor Area Coursework**: Mixed Methods Research",
      col.names = c("CRN",
                    "Title",
                    "Grade",
                    "Credit Hours"),
      align = c('c', 'l', 'c', 'c'))
```

```{r reqr}
reqr <-
    data.frame(
        CRN = c("`PSY 621`",
                "`PSY 618`",
                "`PSY 622`",
                "`PSY 624`"),
        Title = c("_Univariate Quantitative Methods_",
                  "_Ethics & Professional Issues in Applied Research and Practice_",
                  "_Multiple Regression & Multivariate Quantitative Methods_",
                  "_Research Design in Applied Psychology_"),
        Grade = c("A-",
                  "A",
                  "B+",
                  "A"),
        Hrs = c(5,
                4,
                5,
                4))

knitr::kable(reqr, caption = "Research Methods & Statistics Coursework Required by Program",
      col.names = c("CRN",
                    "Title",
                    "Grade",
                    "Credit Hours"),
      align = c('c', 'l', 'c', 'c'))
```

```{r prac}
prac <-
    data.frame(
        CRN = c("`PSY 609`",
                "`PSY 609`",
                "`PSY 501`"),
        Title = c("_Prac: Violence Prevention I_",
                  "_Prac: Violence Prevention II_",
                  "_Res: BIP Staff Interviews_"),
        Grade = c("P",
                  "P",
                  "A"),
        Hrs = c(1,
                1,
                6))

knitr::kable(prac, caption = "Research & Field-Based Practica",
      col.names = c("CRN",
                    "Title",
                    "Grade",
                    "Credit Hours"),
      align = c('c', 'l', 'c', 'c'))
```

# (B) Rationale <!--`(1 page)`-->

There are two core components of my action-oriented research framework: (1) a focus on developing and implementing innovative and inclusive research methodologies, data analytic approaches, and dissemenation strategies; and (2) a diligent focus on the importance of critical reflexivity throughout the research process. The action-oriented and values-transparent community psycholgical research approach was born out of a resistence to research methodologies, social policies, and implementation practices that ultimately served to reinforce and/or strengthen social and economic inequalities<!--CITE-->. This foundation necessitates vigilance in critical reflexivity throughout and beyond the research process. The critical literature review I am proposing here is intended to serve this key characterstic of community psychology.

Community psychological theory values the notion that the communities in which research is taking place and/or affecting (whether directly or indirectly) should be as involved as possible in _all_ phases of the research process, rather than solely as anonymous datapoints in the analysis. Community psychology thus favors inclusion over exclusion, participant voices equally with researchers' voices, and participatory and/or purposive sampling methods over convenience sampling methods. The reviewed literature will be evaluated and critiqued according to these types of community psychological standards regarding (1) _research methodologies_, (2) _data anaytic approaches_, (3) _interpretations of findings_, and (4) _research dissemination_.

# (C) Major Area Paper Outline <!--`(2-3 pages)`-->

## I. Background & Significance

I propose conducting a systematic critical review of research conducted with marginalized populations, with a specific focus on violence-related research with sexual minority women (SMW).^[[see relevance to dissertation topic](D-dissertationTopic.html)] The critical review will attempt to map core components of community psychological theory and methodologies to the body of research available under the above-defined content and research discipline scopes. In particular, I am interested in evaluating the extent to which community psychological theory and methodologies are implemented, or not, in research related to the historically marginalized population of interest^[i.e., sexual minority women]. I am further interested in examining how the implementation of community psychological research has evolved over time since the origination of the field, as well as potential trajectories based on the current state of discourse within Community Psychology and closely related research and practice disciplines.


## II. Theoretical Grounding

In a sense, the proposed review's theoretical grounding is best summarized in terms of the of the Community Psychology Practice Council's [_"Theory into Action Bulletin"_](http://www.scra27.org/what-we-do/practice/practice-council-initatives/theory-action-bulletin/)^[[Society for Community Research and Action (SCRA)](http://www.scra27.org/)]. The review will be grounded in theories related to action-oriented research and their applications [@chandler2003transforming; @brydon-miller2003why; @friedman-nimz2006blending; @kelly2004community; @noffke1997professional; @prilleltensky2001value-based; @prilleltensky1997values; @seidman2012emerging], as well as social and community psychological theories related to female same-sex intimate partner violence. In particular, I am interested in the intersections that exist across these theoretical, methodological, and problem-specific domains in terms of their actual applications and manifestations in various settings. Below is a list of theoretical and conceptual frameworks specifically guiding the proposed review.

### Theory Specific to Community Psychology (CP):

- _The Action Research Cycle & Community-Based Participatory Action Research_ [CBPR; @fine2004participatory; @chandler2003transforming; @brydon-miller2003why; @friedman-nimz2006blending; @kelly2004community; @noffke1997professional; @prilleltensky2001value-based; @prilleltensky1997values; @seidman2012emerging; @anders1966action]
- _Ecological systems theory and the Social Ecological Model_ [@stokols1996translating; @visser2007social; @walker2006handful; @centers2015social; @kloos2009social; @anderies2004framework; @baral2013modified; @stokols1996translating]
- _Community Empowerment & Individual Empowerment_ [@speer1995community; @riger1993what; @beeker1998community; @cobb1993empowerment; @collins2002black]
- _[Community] Health Promotion_ [@stokols1996translating]


### Theory Related to both Community Psychology and IPV Intervention and Prevention:

- _Coordinated Community Response_ [CCR; @gondolf2007theoretical; @barner2011interventions; @dutton2007duluth]
- _Minority Stress Theory & Resilience_ [MS; @meyer2003prejudice; @meyer2010right; @meyer1995minority; @meyer2015resilience]
- _Risk Factors vs. Protective Factors_ [@baral2013modified; @whitaker2014linking; @tharp2013systematic; @walton-moss2005risk; @heckert2004battered]

### Intersecting Community Psychology Theory & Research Methodology

- _Grounded Theory Methods_ [@charmaz2006constructing; @corbin1990basics; @strauss1994grounded]
- _Mixed-Methods Research_ [@morgan2014mmr; @creswell2013research; @greene1989toward; @johnson2007toward]
- _Program Evaluation_ [@greene1989toward; @kidder1987qualitative; @mertens2012program; @owen1999program; @royse2009program]

## III. Paper Parameters / Systematic Literature Review Methodology

### A. Key literature search strategy

The scope of reviewed research will include published work in the Community Psychology discipline, as well as research published in related fields such as Social and Clinical Psychology, Social Work, Public Health, and Sociology.

### B. Focal data bases

The collection process will primarily utilize the robust literature search capabilities provided by **Google Scholar**. In addition, resources specific to community psychology, such as ["The Community Toolbox" (TCB)](http://ctb.ku.edu/en), will be surveyed as potential sources of information for this review.

### C. Key search terms.

Key search terms will focus on both the focal research content area for this paper (i.e., female same-sex intimate partner vioelence) and terms related to community-psychological methods or theories. Sample boolean search queries are provied below to demonstrate this aspect of the proposed search methodology.

- `("intimate partner violence" OR "domestic violence") OR (Aggression OR violence) AND (lesbian OR bisexual OR "sexual minority") AND women`
- `female AND "same-sex" AND ("intimate partner violence" OR "domestic violence") AND (intervention OR evaluation)`
- `female AND "same-sex" AND ("intimate partner violence" OR "domestic violence") AND (ecological OR multilevel)`

### D. Inclusion/exclusion criteria

- **Dates published**: Between 1965 & 2016
- **Topics**:
    - Intimate partner violence (IPV) among sexual minority women (causes, correlates, and/or consequences)
    - IPV intervention and/or prevention strategies/approaches
    - IPV intervention and/or prevention program evaluation
- **Research & Practice Fields/Frameworks**:
    - Community Psychology
    - Other Psychology Sub-fields (Social, Clinical, Organizational)
    - Sociology
    - Public Health
    - Social Work

## IV. Methodological Considerations

## V. Integrative Literature Review

## VI. Critique of Literature

### A. Research Methodologies.

Are efforts made to ensure that _all available_ stakeholders' and informants' voices and accessibility considered equally, and that certain voices are not unjustifiably privileged over others?

### B. Interpretations of Findings.

Is feedback from key stakeholders and informants to the research accepted and genuinely considered by the core research team? Are efforts made to ensure that _all available_ stakeholders' and informants' voices and accessibility considered equally, and that certain voices are not unjustifiably privileged over others?

### C. Research Dissemination.

Are key stakeholders and informants to the research given access to reports of a given project's progress and/or findings? Is such access in fact accessible (i.e., free and easy to locate)?


## VII. Summary of Findings

## VIII. Applied Implications


# (D) Relevance to Dissertation Topic <!--`(1 page)`-->

The proposed review paper is motivated by the program of research I have pursued over the past three years. I intend to continue pursuing this program of research via my dissertation. This program of research is focused on developing comprehensive and intersectional intimate partner violence (IPV) prevention strategies specific to the experiences and needs of historically marginalized populations.

## Dissertation Topic Background

My Masters thesis project served as the first phase of this research program. The purposes of this study were to (1) inform the finalization of a working intersectional model of same-gender IPV among sexual minority women, and (2) evaluate the face, construct, content validity, and coverage of existing survey measures related to the model's constructs in terms of their relevance and accuracy to sexual minority women's experiences and identities. A series of in-depth semi-structured, open-ended one-on-one interviews (n=10) and one focus group (ngroup=4) were conducted with fourteen lesbian, gay, bisexual, transgender, and queer (LGBTQ) women in Portland, Oregon. Individuals were recruited and engaged in the study via a combination of purposive and convenience sampling methods aided by involvement of multiple community partners working in violence and education related fields. Interview and focus group questions addressed participants' experiences with gender role stress and minority stress. Grounded theory analysis of participants' narrative responses informed the coverage and relevance of constructs in a working intersectional model predicting women's use of violence in their same-gender intimate relationships. Findings from this analysis support an intersectional and contextually-minded approach to IPV intervention and prevention strategies.

## Intended Dissertation Research

The first exploratory phase's findings and corresponding conclusions will directly inform the work for my dissertation, which will constitute the second phase of this research program. Specifically, I will use insights gained from this first phase of of research to make necessary revisions to the evaluated survey measures, and the modified measures will be used in the second phase of research to collect data from 200-300 LGBTQ women recruited from the greater Portland, OR area. The intersectional model will be subsequently tested for fit using these data, and findings from this second phase will be used in collaboration with local community partners to develop strategies for IPV intervention and prevention specifically tailored to the experiences, identities, and needs of LGBTQ women.

## Proposed Review Paper's Relevance

The theoretical and methodological groundings for the proposed review paper have and continue to serve as guiding frameworks for the above-described program of research. Further, the proposed critical review of community psychological theory and methodology applications aligns with the critical review I conducted as part of my Masters Thesis, which focused on the influence and consequences of second-wave feminism on IPV-related research, activism, policy, and practice. Through the latter critical review process, I developed a comprehensive understanding of the context in which the research area I am pursuing is situated. Similarly, I intend to utilize the proposed review paper as an in-depth critical reflection on the community psychology-specific context in which my dissertation research will be conducted.

# (E) Reading List

@anderies2004framework
- @anders1966action
- @baral2013modified
- @barner2011interventions
- @beeker1998community
- @brydon-miller2003why
- @centers2015social
- @chandler2003transforming
- @charmaz2006constructing
- @cobb1993empowerment
- @collins2002black
- @corbin1990basics
- @creswell2013research
- @dutton2007duluth
- @fine2004participatory
- @friedman-nimz2006blending
- @gondolf2007theoretical
- @greene1989toward
- @heckert2004battered
- @johnson2007toward
- @kelly2004community
- @kidder1987qualitative
- @kloos2009social
- @mertens2012program
- @meyer1995minority
- @meyer2003prejudice
- @meyer2010right
- @meyer2015resilience
- @morgan2014mmr
- @noffke1997professional
- @owen1999program
- @prilleltensky1997values
- @prilleltensky2001value-based
- @riger1993what
- @royse2009program
- @seidman2012emerging
- @speer1995community
- @stokols1996translating
- @strauss1994grounded
- @tharp2013systematic
- @visser2007social
- @walker2006handful
- @walton-moss2005risk
- @whitaker2014linking


# References
