---
title: "<em><code>R</code></em> DataViz Gallery"
---

<style>
body {
    background-color: rgba(0, 0, 0, 0.025);
    width: 95%;
}
p {
    width:95% !important;
}

h1:not(.title) {
    text-align: center;
    margin-top: 3em;
    margin-bottom: 1.5em;
}

h1:not(.title)::after {
    width         : 100%;
    /*margin-top    : 21px;*/
    /*margin-bottom : 21px;*/
    border        : 0;
    height: 1px;
    /*border-top    : 2px solid #3f3f3f;*/
    background-image: linear-gradient(to right, #e6e6e6, #333, #e6e6e6);
}
</style>


```{r setup, echo=FALSE, results='hide', message=FALSE, warning=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = 'asis')

g0 <- list.files(path = "graphics/", pattern = ".*?\\.svg$", recursive = TRUE)
g1 <- g0[!grepl("(zARCHIVE-)|(inputs/)|( copy)", g0)]
g2 <- paste0("graphics/", g1)

ginfo <- file.info(g2)[, c("ctime", "mtime", "atime")]

g <- g2[ginfo$ctime > "2017-05-31"]
glabs_ref <- gsub("(\\w+/){1,}rplot-(.*?)\\.svg", "\\2", g)
# glabs_id <- paste0("#", glabs_path)
# pathPrefix = "graphics/"
Rlightbox <- function(g, glabs) {
    gl <- vector("character", length(g))
    for (i in 1:length(g)) {
        gl[i] <- paste0("<div class='lightbox' href=", glabs[i], "><img src=", g[i], " style=\"width=auto;\" /></div>")
        # <div class='lightbox-target' id=", glabs2[i], "><span class='close cursor' onclick='closeModal()'>&times;</span><img src=", g[i], " /><a class='lightbox-close' href='#'></a></div><a class='prev' onclick='plusSlides(-1)'>&#10094;</a><a class='next' onclick='plusSlides(1)'>&#10095;</a>
    }
    return(gl)
}


library(pander)
panderOptions("p.sep", "\n")
panderOptions("p.copula", "\n")
panderOptions("p.wrap", "")
# pander(gl)

library(Riley); library(ggplot2); library(igraph); library(ggparallel); library(arcdiagram); library(ggthemes); library(Riley)
```

<hr class="Bold"/>
<div style="text-align:center;">
`r Riley::Rcite_r(file = "../auxDocs/REFs.bib", footnote = FALSE, Rnote = "Graphics on this page were created using")`
</div>
<hr class="SemiBold">

# Donut Plot via the **`ggplot2`** package

<div class="gallery cf">

```{r}
gdonut <- g[grepl("donut_", g)]
gdonutlabs2 <- gsub("(\\w+/){1,}(.*?)\\.svg", "\\2", gdonut)
gdonutlabs1 <- paste0("#", gdonutlabs2)
gldonut <- Rlightbox(gdonut, gdonutlabs1)
# for (i in 1:length(gdonut)) {
#     gldonut[i] <- paste0("<a class='lightbox' href=", gdonutlabs1[i], "><img src=", gdonut[i], " /></a><div class='lightbox-target' id=", gdonutlabs2[i], "><img src=", gdonut[i], " /><a class='lightbox-close' href='#'></a></div>")
# }

pander(gldonut)
```

</div>

# Timelines via the **`ggplot2`** package

<div class="gallery cf">

```{r}
gtl <- g[grepl("tl_", g)]
gtllabs2 <- grep("rplot-tl_.*?\\.svg", gtl, value = T)
gtllabs1 <- paste0("#", gtllabs2)
gltl <- Rlightbox(gtl, gtllabs1)

# for (i in 1:length(gtl)) {
    # gltl[i] <- paste0("<a class='lightbox' href=", gtllabs1[i], "><img src=", gtl[i], " /></a><div class='lightbox-target' id=", gtllabs2[i], "><img src=", gtl[i], " /><a class='lightbox-close' href='#'></a></div>")
# }

pander(gltl)
```

</div>

# Histogram Timeline via **`Base R Graphics`**

<div class="gallery cf">

```{r}
gtlhist <- g[grepl("hist_", g)]
gtlhistlabs2 <- grep("rplot-hist_.*?\\.svg", gtlhist, value = T)
gtlhistlabs1 <- paste0("#", gtlhistlabs2)
gltlhist <- Rlightbox(gtlhist, gtlhistlabs1)
# for (i in 1:length(gtlhist)) {
    # gltlhist[i] <- paste0("<a class='lightbox' href=", gtlhistlabs1[i], "><img src=", gtlhist[i], " /></a><div class='lightbox-target' id=", gtlhistlabs2[i], "><img src=", gtlhist[i], " /><a class='lightbox-close' href='#'></a></div>")
# }

pander(gltlhist)
```

</div>

# Dot plots^[@robbins2006dot;@cleveland1984graphical] via My _in Progress_ **`Riley`** Package

<div class="gallery cf">

```{r}
gdot <- g[grepl("dot_", g)]
gdotlabs2 <- grep("rplot-dot_.*?\\.svg", gdot, value = T)
gdotlabs1 <- paste0("#", gdotlabs2)
gldot <- Rlightbox(gdot, gdotlabs1)

# for (i in 1:length(gdot)) {
    # gldot[i] <- paste0("<a class='lightbox' href=", gdotlabs1[i], "><img src=", gdot[i], " onclick='openModal();' /></a><div class='lightbox-target' id=", gdotlabs2[i], "><span class='close cursor' onclick='closeModal()'>&times;</span><img src=", gdot[i], " /><a class='lightbox-close' href='#'></a></div><a class='prev' onclick='plusSlides(-1)'>&#10094;</a><a class='next' onclick='plusSlides(1)'>&#10095;</a>")
# }

pander(gldot)
```

</div>

# Parallel Sets via the **`ggplot2`** package

<div class="gallery cf">

```{r}
gparset <- g[grepl("parset_", g)]
gparsetlabs2 <- grep("rplot-parset_.*?\\.svg", gparset, value = T)
gparsetlabs1 <- paste0("#", gparsetlabs2)
glparset <- Rlightbox(gparset, gparsetlabs1)

# for (i in 1:length(gparset)) {
    # glparset[i] <- paste0("<a class='lightbox' href=", gparsetlabs1[i], "><img src=", gparset[i], " /></a><div class='lightbox-target' id=", gparsetlabs2[i], "><img src=", gparset[i], " /><a class='lightbox-close' href='#'></a></div>")
# }

pander(glparset)
```

</div>

# Network Diagrams via the **`igraph`** & **`arcdiagram`**

<div class="gallery cf">

```{r}
garc0 <- list.files(path = "graphics/", pattern = ".*?\\.png$", recursive = TRUE)
garc1 <- garc0[!grepl("(zARCHIVE-)|(inputs/)|( copy)", garc0)]
garc2 <- paste0("graphics/", garc1)

garcinfo <- file.info(garc2)[, c("ctime", "mtime", "atime")]

garc3 <- garc2[garcinfo$ctime > "2017-05-31"]

gnet <- g[grepl("net_", g)]
garc <- garc3[grepl("arc_", garc3)]
gnets <- c(gnet, garc)
gnetslabs21 <- grep("rplot-net_.*?\\.svg", gnets, value = T)
gnetslabs22 <- grep("rplot-arc_.*?\\.png", gnets, value = T)
gnetslabs2 <- c(gnetslabs21, gnetslabs22)
gnetslabs1 <- paste0("#", gnetslabs2)
glnets <- Rlightbox(gnets, gnetslabs1)
# for (i in 1:length(gnets)) {
    # glnets[i] <- paste0("<a class='lightbox' href=", gnetslabs1[i], "><img src=", gnets[i], " /></a><div class='lightbox-target' id=", gnetslabs2[i], "><img src=", gnets[i], " /><a class='lightbox-close' href='#'></a></div>")
# }

pander(glnets)
```

# Hierarchical Cluster Analysis Dendrograms & Related Barplots via **`Base R Graphics`**

```{r}
ghclust <- g[grepl("hclust_", g)]
ghclustlabs2 <- grep("rplot-hclust_.*?\\.svg", ghclust, value = T)
ghclustlabs1 <- paste0("#", ghclustlabs2)
glhclust <- Rlightbox(ghclust, ghclustlabs1)

pander(glhclust)
```

# K-Means & Fuzzy Analysis Clustering Graphics via the **`Cluster`** Package

```{r}
gkclust <- g[grepl("kclust_", g)]
gkclustlabs2 <- grep("rplot-kclust_.*?\\.svg", gkclust, value = T)
gkclustlabs1 <- paste0("#", gkclustlabs2)
glkclust <- Rlightbox(gkclust, gkclustlabs1)

pander(glkclust)
```

</div>

<hr class="Bold">

<h1 style="text-align:left;margin-top:-1em;">References</h1>
<div class="refs">
