---
title: "Literature Search Notes"
author: "Riley M. Smith"
date: "`r format(Sys.Date(), '%d %B %Y')`"
---

```{r setup, echo=FALSE, results='hide', message=FALSE, warning=FALSE, cache=FALSE}
source("../SETUP.R")
knitr::opts_chunk$set(
    tidy = FALSE,
    echo = TRUE,
    fig.keep = 'high',
    fig.show = 'hold',
    results = 'asis',
    echoRule = TRUE
)
rpm()
j.v <- c("Journal of Interpersonal Violence", "Violence Against Women", "Violence and Victims")

j.cp <- c("Action Research", "American Journal of Community Psychology", "American Journal of Health Promotion", "American Journal of Orthopsychiatry", "American Journal of Preventive Medicine", "American Journal of Public Health", "Australian Community Psychologist", "Community Development", "Community Development Journal", "Community Mental Health Journal", "Community Psychology in Global Perspective", "Cultural Diversity \\& Ethnic Minority Psychology", "Global Journal of Community Psychology Practice", "Health Education \\& Behavior", "Health Promotion Practice", "Journal of Applied Social Psychology", "Journal of Community \\& Applied Social Psychology", "Journal of Community Practice", "Journal of Community Psychology", "Journal of Health \\& Social Behavior", "Journal of Prevention \\& Intervention", "Journal of Primary Prevention", "Journal of Rural Community Psychology", "Journal of Social Issues", "Psychiatric Rehabilitation Journal", "Psychology of Women Quarterly", "Social Science \\& Medicine", "The Community Psychologist", "Transcultural Psychiatry", "Progress in Community Health Partnerships: Research, Education, \\& Action")
```

# II.A. Key literature search strategy

Six separate literature searches were conducted using the [_PsycINFO_](http://www.apa.org/pubs/databases/psycinfo/) and [_Web of Science_](http://wokinfo.com) online citation indexing databases via the [Portland State University library website](library.pdx.edu):

- S1: Intimate Partner Violence (including Domestic Violence & Partner Abuse) - General^[\texttt{SU("intimate partner violence" OR "domestic violence" OR "partner abuse")}]
- S2: Intimate Partner Violence (including Domestic Violence & Partner Abuse) Interventions^[\texttt{SU("intimate partner violence" OR "domestic violence" OR "partner abuse") AND SU("intervention")")}]
- S3 - Intimate Partner Violence (including Domestic Violence & Partner Abuse) Intervention Evaluations^[\texttt{SU("intimate partner violence" OR "domestic violence" OR "partner abuse") AND SU("intervention")}]
- S4 - Female Same-Sex/Same-Gender Intimate Partner Violence^[\texttt{SU("intimate partner violence" OR "domestic violence" OR "partner abuse") AND SU("Lesbian")}]
- S5 - Female Same-Sex/Same-Gender Intimate Partner Violence Interventions^[\texttt{SU("intimate partner violence" OR "domestic violence" OR "partner abuse") AND SU("Lesbian") AND SU("intervention")}]
- S6 - Female Same-Sex/Same-Gender Intimate Partner Violence Intervention Evaluations^[\texttt{SU("intimate partner violence" OR "domestic violence" OR "partner abuse") AND SU("Same-Sex" OR "Same-Gender" OR "Lesbian") AND SU("intervention" OR "evaluation")}]

Each search was restricted to the following articles published within the following scholarly journals:

\tdef{1. Violence-related journals:}{`r j.v`}

\tdef{2. Community Psychology-specific journals:}{`r j.cp`}

Each database search was further restricted to empirical studies published between 1965 and 2017 [i.e., the year of the [Swampscott conference](http://www.scra27.org/publications/tcp/tcp-past-issues/tcpsummer2014/remembering-swampscott/) and the present year; @fryer2008some]. All searches restricted to 1. scholarly journals ('source type') \& 2. journal articles ('record type'), excluding 'Systematic Review' and 'Literature Review' methodologies.

\newpage

# Search Notes

\Frule

# S1 - Intimate Partner Violence (including "Domestic Violence" \& "Partner Abuse") - General

## PsycINFO

> SU("intimate partner violence" OR "domestic violence" OR "partner abuse") AND YR(>1965) AND PUBALL("Journal of Interpersonal Violence" OR "Violence Against Women" OR "Journal of Family Violence" OR "Violence and Victims" OR "Aggression and Violent Behavior" OR "Partner Abuse" OR "Trauma, Violence, & Abuse" OR "Psychology of Violence" OR "Journal of Emotional Abuse" OR "Response to the Victimization of Women & Children" OR "Action Research" OR "American Journal of Community Psychology" OR "American Journal of Health Promotion" OR "American Journal of Orthopsychiatry" OR "American Journal of Preventive Medicine" OR "American Journal of Public Health" OR "Australian Community Psychologist" OR "Community Development" OR "Community Development Journal" OR "Community Mental Health Journal" OR "Community Psychology in Global Perspective" OR "Cultural Diversity & Ethnic Minority Psychology" OR "Global Journal of Community Psychology Practice" OR "Health Education & Behavior" OR "Health Promotion Practice" OR "Journal of Applied Social Psychology" OR "Journal of Community & Applied Social Psychology" OR "Journal of Community Practice" OR "Journal of Community Psychology" OR "Journal of Health & Social Behavior" OR "Journal of Prevention & Intervention" OR "Journal of Primary Prevention" OR "Journal of Rural Community Psychology" OR "Journal of Social Issues" OR "Psychiatric Rehabilitation Journal" OR "Psychology of Women Quarterly" OR "Social Science & Medicine" OR "The Community Psychologist" OR "Transcultural Psychiatry" OR "Progress in Community Health Partnerships: Research, Education, & Action") NOT ME("Systematic Review" OR "Literature Review")

```{r }
s1.n <- 4386
```

## Web of Science ("`S1w`")

> TS=("intimate partner violence" OR "domestic violence" OR "partner abuse") AND PY=(1965-2017) AND SO=("Journal of Interpersonal Violence" OR "Violence Against Women" OR "Journal of Family Violence" OR "Violence and Victims" OR "Aggression and Violent Behavior" OR "Partner Abuse" OR "Trauma, Violence, & Abuse" OR "Psychology of Violence" OR "Journal of Emotional Abuse" OR "Response to the Victimization of Women & Children" OR "Action Research" OR "American Journal of Community Psychology" OR "American Journal of Health Promotion" OR "American Journal of Orthopsychiatry" OR "American Journal of Preventive Medicine" OR "American Journal of Public Health" OR "Australian Community Psychologist" OR "Community Development" OR "Community Development Journal" OR "Community Mental Health Journal" OR "Community Psychology in Global Perspective" OR "Cultural Diversity & Ethnic Minority Psychology" OR "Global Journal of Community Psychology Practice" OR "Health Education & Behavior" OR "Health Promotion Practice" OR "Journal of Applied Social Psychology" OR "Journal of Community & Applied Social Psychology" OR "Journal of Community Practice" OR "Journal of Community Psychology" OR "Journal of Health & Social Behavior" OR "Journal of Prevention & Intervention" OR "Journal of Primary Prevention" OR "Journal of Rural Community Psychology" OR "Journal of Social Issues" OR "Psychiatric Rehabilitation Journal" OR "Psychology of Women Quarterly" OR "Social Science & Medicine" OR "The Community Psychologist" OR "Transcultural Psychiatry" OR "Progress in Community Health Partnerships: Research, Education, & Action") NOT DT=("Review" OR "Proceedings Paper")

```{r }
s1w.n <- 3376
s1 <- range(c(s1.n, s1w.n))
```

------

\[ S1~~Results = `r paste0(comma(s1[1]), "-", comma(s1[2]))` \]

\newpage

# S2 - Intimate Partner Violence (including "Domestic Violence" \& "Partner Abuse") Interventions

## PsycINFO

> SU("intimate partner violence" OR "domestic violence" OR "partner abuse") AND SU("intervention") AND YR(>1965) AND PUBALL("Journal of Interpersonal Violence" OR "Violence Against Women" OR "Journal of Family Violence" OR "Violence and Victims" OR "Aggression and Violent Behavior" OR "Partner Abuse" OR "Trauma, Violence, & Abuse" OR "Psychology of Violence" OR "Journal of Emotional Abuse" OR "Response to the Victimization of Women & Children" OR "Action Research" OR "American Journal of Community Psychology" OR "American Journal of Health Promotion" OR "American Journal of Orthopsychiatry" OR "American Journal of Preventive Medicine" OR "American Journal of Public Health" OR "Australian Community Psychologist" OR "Community Development" OR "Community Development Journal" OR "Community Mental Health Journal" OR "Community Psychology in Global Perspective" OR "Cultural Diversity & Ethnic Minority Psychology" OR "Global Journal of Community Psychology Practice" OR "Health Education & Behavior" OR "Health Promotion Practice" OR "Journal of Applied Social Psychology" OR "Journal of Community & Applied Social Psychology" OR "Journal of Community Practice" OR "Journal of Community Psychology" OR "Journal of Health & Social Behavior" OR "Journal of Prevention & Intervention" OR "Journal of Primary Prevention" OR "Journal of Rural Community Psychology" OR "Journal of Social Issues" OR "Psychiatric Rehabilitation Journal" OR "Psychology of Women Quarterly" OR "Social Science & Medicine" OR "The Community Psychologist" OR "Transcultural Psychiatry" OR "Progress in Community Health Partnerships: Research, Education, & Action") NOT ME("Systematic Review" OR "Literature Review")


```{r }
s2.n <- 337
```

## Web of Science ("`S2w`")

> TS=("intimate partner violence" OR "domestic violence" OR "partner abuse") AND TS=("intervention") AND PY=(1965-2017) AND SO=("Journal of Interpersonal Violence" OR "Violence Against Women" OR "Journal of Family Violence" OR "Violence and Victims" OR "Aggression and Violent Behavior" OR "Partner Abuse" OR "Trauma, Violence, & Abuse" OR "Psychology of Violence" OR "Journal of Emotional Abuse" OR "Response to the Victimization of Women & Children" OR "Action Research" OR "American Journal of Community Psychology" OR "American Journal of Health Promotion" OR "American Journal of Orthopsychiatry" OR "American Journal of Preventive Medicine" OR "American Journal of Public Health" OR "Australian Community Psychologist" OR "Community Development" OR "Community Development Journal" OR "Community Mental Health Journal" OR "Community Psychology in Global Perspective" OR "Cultural Diversity & Ethnic Minority Psychology" OR "Global Journal of Community Psychology Practice" OR "Health Education & Behavior" OR "Health Promotion Practice" OR "Journal of Applied Social Psychology" OR "Journal of Community & Applied Social Psychology" OR "Journal of Community Practice" OR "Journal of Community Psychology" OR "Journal of Health & Social Behavior" OR "Journal of Prevention & Intervention" OR "Journal of Primary Prevention" OR "Journal of Rural Community Psychology" OR "Journal of Social Issues" OR "Psychiatric Rehabilitation Journal" OR "Psychology of Women Quarterly" OR "Social Science & Medicine" OR "The Community Psychologist" OR "Transcultural Psychiatry" OR "Progress in Community Health Partnerships: Research, Education, & Action") NOT DT=("Review" OR "Proceedings Paper")

```{r }
s2w.n <- 686
s2 <- range(c(s2.n, s2w.n))
```

------

\[ S2~~Results = `r paste0(comma(s2[1]), "-", comma(s2[2]))` \]

\newpage

# S3 - Intimate Partner Violence Intervention Evaluations

## PsycINFO

> SU("intimate partner violence" OR "domestic violence" OR "partner abuse") AND SU("intervention" AND "evaluation") AND YR(>1965) AND PUBALL("Journal of Interpersonal Violence" OR "Violence Against Women" OR "Violence and Victims" OR "Action Research" OR "American Journal of Community Psychology" OR "American Journal of Health Promotion" OR "American Journal of Orthopsychiatry" OR "American Journal of Preventive Medicine" OR "American Journal of Public Health" OR "Australian Community Psychologist" OR "Community Development" OR "Community Development Journal" OR "Community Mental Health Journal" OR "Community Psychology in Global Perspective" OR "Cultural Diversity & Ethnic Minority Psychology" OR "Global Journal of Community Psychology Practice" OR "Health Education & Behavior" OR "Health Promotion Practice" OR "Journal of Applied Social Psychology" OR "Journal of Community & Applied Social Psychology" OR "Journal of Community Practice" OR "Journal of Community Psychology" OR "Journal of Health & Social Behavior" OR "Journal of Prevention & Intervention" OR "Journal of Primary Prevention" OR "Journal of Rural Community Psychology" OR "Journal of Social Issues" OR "Psychiatric Rehabilitation Journal" OR "Psychology of Women Quarterly" OR "Social Science & Medicine" OR "The Community Psychologist" OR "Transcultural Psychiatry" OR "Progress in Community Health Partnerships: Research, Education, & Action") NOT ME("Systematic Review" OR "Literature Review")


```{r }
s3.n <- 32
```

## Web of Science ("`S3w`")

> TS=("intimate partner violence" OR "domestic violence" OR "partner abuse") AND TS=("intervention" AND "evaluation") AND PY=(1965-2017) AND SO=("Journal of Interpersonal Violence" OR "Violence Against Women" OR "Violence and Victims" OR "Action Research" OR "American Journal of Community Psychology" OR "American Journal of Health Promotion" OR "American Journal of Orthopsychiatry" OR "American Journal of Preventive Medicine" OR "American Journal of Public Health" OR "Australian Community Psychologist" OR "Community Development" OR "Community Development Journal" OR "Community Mental Health Journal" OR "Community Psychology in Global Perspective" OR "Cultural Diversity & Ethnic Minority Psychology" OR "Global Journal of Community Psychology Practice" OR "Health Education & Behavior" OR "Health Promotion Practice" OR "Journal of Applied Social Psychology" OR "Journal of Community & Applied Social Psychology" OR "Journal of Community Practice" OR "Journal of Community Psychology" OR "Journal of Health & Social Behavior" OR "Journal of Prevention & Intervention" OR "Journal of Primary Prevention" OR "Journal of Rural Community Psychology" OR "Journal of Social Issues" OR "Psychiatric Rehabilitation Journal" OR "Psychology of Women Quarterly" OR "Social Science & Medicine" OR "The Community Psychologist" OR "Transcultural Psychiatry" OR "Progress in Community Health Partnerships: Research, Education, & Action") NOT DT=("Review" OR "Proceedings Paper")


```{r echo=FALSE}
s3w.n <- 46
s3 <- range(c(s3.n, s3w.n))
```

------

\[ S3~~Results = `r paste0(comma(s3[1]), "-", comma(s3[2]))` \]

\newpage

# S4 - Female Same-Sex/Same-Gender Intimate Partner Violence

## PsycINFO

> SU("intimate partner violence" OR "domestic violence" OR "partner abuse") AND SU("Same-Sex" OR "Same-Gender") AND SU("women" OR "female" OR "lesbian") AND YR(>1965) AND PUBALL("Journal of Interpersonal Violence" OR "Violence Against Women" OR "Violence and Victims" OR "Action Research" OR "American Journal of Community Psychology" OR "American Journal of Health Promotion" OR "American Journal of Orthopsychiatry" OR "American Journal of Preventive Medicine" OR "American Journal of Public Health" OR "Australian Community Psychologist" OR "Community Development" OR "Community Development Journal" OR "Community Mental Health Journal" OR "Community Psychology in Global Perspective" OR "Cultural Diversity & Ethnic Minority Psychology" OR "Global Journal of Community Psychology Practice" OR "Health Education & Behavior" OR "Health Promotion Practice" OR "Journal of Applied Social Psychology" OR "Journal of Community & Applied Social Psychology" OR "Journal of Community Practice" OR "Journal of Community Psychology" OR "Journal of Health & Social Behavior" OR "Journal of Prevention & Intervention" OR "Journal of Primary Prevention" OR "Journal of Rural Community Psychology" OR "Journal of Social Issues" OR "Psychiatric Rehabilitation Journal" OR "Psychology of Women Quarterly" OR "Social Science & Medicine" OR "The Community Psychologist" OR "Transcultural Psychiatry" OR "Progress in Community Health Partnerships: Research, Education, & Action") NOT ME("Systematic Review" OR "Literature Review")

```{r }
s4.n <- 18
```

## Web of Science ("`S4w`")

> TS=("intimate partner violence" OR "domestic violence" OR "partner abuse") AND TS=("Same-Sex" OR "Same-Gender") AND TS=("women" OR "female" OR "lesbian") AND PY=(1965-2017) AND SO=("Journal of Interpersonal Violence" OR "Violence Against Women" OR "Violence and Victims" OR "Action Research" OR "American Journal of Community Psychology" OR "American Journal of Health Promotion" OR "American Journal of Orthopsychiatry" OR "American Journal of Preventive Medicine" OR "American Journal of Public Health" OR "Australian Community Psychologist" OR "Community Development" OR "Community Development Journal" OR "Community Mental Health Journal" OR "Community Psychology in Global Perspective" OR "Cultural Diversity & Ethnic Minority Psychology" OR "Global Journal of Community Psychology Practice" OR "Health Education & Behavior" OR "Health Promotion Practice" OR "Journal of Applied Social Psychology" OR "Journal of Community & Applied Social Psychology" OR "Journal of Community Practice" OR "Journal of Community Psychology" OR "Journal of Health & Social Behavior" OR "Journal of Prevention & Intervention" OR "Journal of Primary Prevention" OR "Journal of Rural Community Psychology" OR "Journal of Social Issues" OR "Psychiatric Rehabilitation Journal" OR "Psychology of Women Quarterly" OR "Social Science & Medicine" OR "The Community Psychologist" OR "Transcultural Psychiatry" OR "Progress in Community Health Partnerships: Research, Education, & Action") NOT DT=("Review" OR "Proceedings Paper")

```{r echo=FALSE}
s4w.n <- 34
s4 <- range(c(s4.n, s4w.n))
```

-----

\[ S4~~Results = `r paste0(comma(s4[1]), "-", comma(s4[2]))` \]

\newpage

# S5 - Female Same-Sex/Same-Gender Intimate Partner Violence Interventions

## PsycINFO

> SU("intimate partner violence" OR "domestic violence" OR "partner abuse") AND SU("Same-Sex" OR "Same-Gender") AND SU("women" OR "female" OR "lesbian") AND SU("intervention"),YR(>1965),PUBALL("Journal of Interpersonal Violence" OR "Violence Against Women" OR "Violence and Victims" OR "Action Research" OR "American Journal of Community Psychology" OR "American Journal of Health Promotion" OR "American Journal of Orthopsychiatry" OR "American Journal of Preventive Medicine" OR "American Journal of Public Health" OR "Australian Community Psychologist" OR "Community Development" OR "Community Development Journal" OR "Community Mental Health Journal" OR "Community Psychology in Global Perspective" OR "Cultural Diversity & Ethnic Minority Psychology" OR "Global Journal of Community Psychology Practice" OR "Health Education & Behavior" OR "Health Promotion Practice" OR "Journal of Applied Social Psychology" OR "Journal of Community & Applied Social Psychology" OR "Journal of Community Practice" OR "Journal of Community Psychology" OR "Journal of Health & Social Behavior" OR "Journal of Prevention & Intervention" OR "Journal of Primary Prevention" OR "Journal of Rural Community Psychology" OR "Journal of Social Issues" OR "Psychiatric Rehabilitation Journal" OR "Psychology of Women Quarterly" OR "Social Science & Medicine" OR "The Community Psychologist" OR "Transcultural Psychiatry" OR "Progress in Community Health Partnerships: Research, Education, & Action") NOT ME("Systematic Review" OR "Literature Review")

```{r echo=FALSE}
s5.n <- 0
```

## Web of Science (`S5w`)

> TS=("intimate partner violence" OR "domestic violence" OR "partner abuse") AND TS=("Same-Sex" OR "Same-Gender") AND TS=("women" OR "female" OR "lesbian") AND TS=("intervention") AND PY=(1965-2017) AND SO=("Journal of Interpersonal Violence" OR "Violence Against Women" OR "Violence and Victims" OR "Action Research" OR "American Journal of Community Psychology" OR "American Journal of Health Promotion" OR "American Journal of Orthopsychiatry" OR "American Journal of Preventive Medicine" OR "American Journal of Public Health" OR "Australian Community Psychologist" OR "Community Development" OR "Community Development Journal" OR "Community Mental Health Journal" OR "Community Psychology in Global Perspective" OR "Cultural Diversity & Ethnic Minority Psychology" OR "Global Journal of Community Psychology Practice" OR "Health Education & Behavior" OR "Health Promotion Practice" OR "Journal of Applied Social Psychology" OR "Journal of Community & Applied Social Psychology" OR "Journal of Community Practice" OR "Journal of Community Psychology" OR "Journal of Health & Social Behavior" OR "Journal of Prevention & Intervention" OR "Journal of Primary Prevention" OR "Journal of Rural Community Psychology" OR "Journal of Social Issues" OR "Psychiatric Rehabilitation Journal" OR "Psychology of Women Quarterly" OR "Social Science & Medicine" OR "The Community Psychologist" OR "Transcultural Psychiatry" OR "Progress in Community Health Partnerships: Research, Education, & Action") NOT DT=("Review" OR "Proceedings Paper")

```{r echo=FALSE}
s5w.n <- 4
s5 <- range(c(s5.n, s5w.n))
```

-----

\[ S5~~Results = `r paste0(comma(s5[1]), "-", comma(s5[2]))` \]

\newpage

# S6 - Female Same-Sex/Same-Gender Intimate Partner Violence Interventions

## PsycINFO

> SU("intimate partner violence" OR "domestic violence" OR "partner abuse") AND SU("Same-Sex" OR "Same-Gender") AND SU("women" OR "female" OR "lesbian") AND SU("intervention" AND "evaluation"),YR(>1965),PUBALL("Journal of Interpersonal Violence" OR "Violence Against Women" OR "Violence and Victims" OR "Action Research" OR "American Journal of Community Psychology" OR "American Journal of Health Promotion" OR "American Journal of Orthopsychiatry" OR "American Journal of Preventive Medicine" OR "American Journal of Public Health" OR "Australian Community Psychologist" OR "Community Development" OR "Community Development Journal" OR "Community Mental Health Journal" OR "Community Psychology in Global Perspective" OR "Cultural Diversity & Ethnic Minority Psychology" OR "Global Journal of Community Psychology Practice" OR "Health Education & Behavior" OR "Health Promotion Practice" OR "Journal of Applied Social Psychology" OR "Journal of Community & Applied Social Psychology" OR "Journal of Community Practice" OR "Journal of Community Psychology" OR "Journal of Health & Social Behavior" OR "Journal of Prevention & Intervention" OR "Journal of Primary Prevention" OR "Journal of Rural Community Psychology" OR "Journal of Social Issues" OR "Psychiatric Rehabilitation Journal" OR "Psychology of Women Quarterly" OR "Social Science & Medicine" OR "The Community Psychologist" OR "Transcultural Psychiatry" OR "Progress in Community Health Partnerships: Research, Education, & Action") NOT ME("Systematic Review" OR "Literature Review")

```{r echo=FALSE}
s6.n <- 0
```

## Web of Science (`S6w`)

> TS=("intimate partner violence" OR "domestic violence" OR "partner abuse") AND TS=("Same-Sex" OR "Same-Gender") AND TS=("women" OR "female" OR "lesbian") AND TS=("intervention" AND "evaluation") AND PY=(1965-2017) AND SO=("Journal of Interpersonal Violence" OR "Violence Against Women" OR "Violence and Victims" OR "Action Research" OR "American Journal of Community Psychology" OR "American Journal of Health Promotion" OR "American Journal of Orthopsychiatry" OR "American Journal of Preventive Medicine" OR "American Journal of Public Health" OR "Australian Community Psychologist" OR "Community Development" OR "Community Development Journal" OR "Community Mental Health Journal" OR "Community Psychology in Global Perspective" OR "Cultural Diversity & Ethnic Minority Psychology" OR "Global Journal of Community Psychology Practice" OR "Health Education & Behavior" OR "Health Promotion Practice" OR "Journal of Applied Social Psychology" OR "Journal of Community & Applied Social Psychology" OR "Journal of Community Practice" OR "Journal of Community Psychology" OR "Journal of Health & Social Behavior" OR "Journal of Prevention & Intervention" OR "Journal of Primary Prevention" OR "Journal of Rural Community Psychology" OR "Journal of Social Issues" OR "Psychiatric Rehabilitation Journal" OR "Psychology of Women Quarterly" OR "Social Science & Medicine" OR "The Community Psychologist" OR "Transcultural Psychiatry" OR "Progress in Community Health Partnerships: Research, Education, & Action") NOT DT=("Review" OR "Proceedings Paper")

```{r echo=FALSE}
s6w.n <- 2
s6 <- range(c(s6.n, s6w.n))
```

-----

\[ S6~~Results = `r paste0(comma(s6[1]), "-", comma(s6[2]))` \]

\newpage

# References
