---
title: "Comprehensive Examination: Major Area Paper Proposal"
author: "Rachel M. Smith"
date: "`r format(Sys.Date, '%d %B %Y')`"
---

\newpage
# (A) Completed Foundational Coursework

# Major,  Minor,  \& Core Program Requirements

`r margin_note("\\textit{Note: '\\textsuperscript{*}' denotes courses applicable to both the major and minor areas.}")`

```{r}
maj <-
    data.frame(
        CRN = c("`PSY 610`",
                "`PSY 614`",
                "`PSY 610`",
                "`PSY 597`",
                "`PSY 510`"),
        Title = c("_Top: Community \\& Social Interventions_",
                  "_Advanced Applied Social Psychology \\& Community Psychology_",
                  "_Top: Program Evaluation^`*`^_",
                  "_Applied Survey Research^`*`^_",
                  "_Top: Place-Based Research^`*`^_"),
        Grade = c("**B+**",
                  "**A**",
                  "**A**",
                  "**A-**",
                  "**A**"),
        Hrs = rep(4, 5))

kable(maj, caption = "**Major Area Coursework**: Applied
      Social \\& Community Psychology",
      col.names = c("CRN",
                    "Title",
                    "Grade",
                    "Credit Hours"),
      align = c('c', 'l', 'c', 'c'))
```

```{r}
minr <-
    data.frame(
        CRN = c("`SOC 610`",
                "`PSY 610`",
                "`SOC 610`",
                "`PSY 510`",
                "`SOC 610`",
                "`PSY 597`",
                "`PSY 510`"),
        Title = c("_Focus Groups_",
                  "_Program Evaluation^`*`^_",
                  "_Qualitative Data Analysis_",
                  "_HLM/Mixed Effects Models for Longitudinal Data Analysis_",
                  "_Mixed Methods Research_",
                  "_Applied Survey Research^`*`^_",
                  "_Place-Based Research^`*`^_",
                  "__"),
        Grade = c("**A**",
                  "**A**",
                  "**A**",
                  "**A**",
                  "**A**",
                  "**A-**",
                  "**A**"),
        Hrs = rep(4, 7))

kable(minr, caption = "**Minor Area Coursework**: Mixed Methods Research",
      col.names = c("CRN",
                    "Title",
                    "Grade",
                    "Credit Hours"),
      align = c('c', 'l', 'c', 'c'))
```

```{r}
reqr <-
    data.frame(
        CRN = c("`PSY 621`",
                "`PSY 618`",
                "`PSY 622`",
                "`PSY 624`"),
        Title = c("_Univariate Quantitative Methods_",
                  "_Ethics \\& Professional Issues in Applied Research and Practice_",
                  "_Multiple Regression \\& Multivariate Quantitative Methods_",
                  "_Research Design in Applied Psychology_"),
        Grade = c("**A-*",
                  "**A**",
                  "**B+*",
                  "**A**"),
        Hrs = c(5,
                4,
                5,
                4))

kable(reqr, caption = "Research Methods \\& Statistics Coursework Required by Program",
      col.names = c("CRN",
                    "Title",
                    "Grade",
                    "Credit Hours"),
      align = c('c', 'l', 'c', 'c'))
```
```{r}
prac <-
    data.frame(
        CRN = c("`PSY 609`",
                "`PSY 609`",
                "`PSY 501`"),
        Title = c("_Prac: Violence Prevention I_",
                  "_Prac: Violence Prevention II_",
                  "_Res: BIP Staff Interviews_"),
        Grade = c("**P**",
                  "**P**",
                  "**A**"),
        Hrs = c(1,
                1,
                6))

kable(prac, caption = "Research \\& Field-Based Practica",
      col.names = c("CRN",
                    "Title",
                    "Grade",
                    "Credit Hours"),
      align = c('c', 'l', 'c', 'c'))
```


\newpage
# (B) Significance \& Rationale `(1 page)`

\todo


\newpage
# (C) Major Area Paper Outline (2-3 pages)

\todo

# I. Background \& Significance
# II. Theoretical Grounding
# III. Paper Parameters / Systematic Literature Review Methodology
- Key literature search strategy
- Focal data bases
- Key search terms
- Inclusion/exclusion criteria

# IV. Methodological Considerations
# V. Integrative Literature Review
# VI. Critique of Literature Strengths \& Limitations
# VII. Summary of Findings
# VIII. Applied Implications


\newpage
# (D) Relevance to Dissertation Topic `(1 page)`

\todo


\newpage
# (E) Reading List

\todo
<!-- SEE BIBTEX BIBLIOGRAPHY GENERATED FOR COMMPSY COHORT -->


# Overview
<!-- This is not a required section for the MAP proposal, and is currently more of a place for me to organize my thoughts -->

## Community Psychology Lens \todo


# IX. References
