---
title: "Integrating Theory, Methods, & Social Justice"
author: "Rachel M. Smith"
date: "`r format(Sys.Date(), '%d %B %Y')`"
---

<!-- >>>>>>> EDITING MARKUP PATTERN: ... <<<<<<<<<<<<<<< -->

```{r setup, echo=FALSE, results='hide', message=FALSE, warning=FALSE, cache=FALSE, fig.show='none', fig.keep='none'}
source("bibs.R")
knitr::opts_chunk$set(echo=FALSE)
```

The purpose of this review is to provide a systematic critical methodological overview of the available empirical research related to intimate partner violence (IPV) intervention and prevention efforts through a community psychological lens. This review is specifically focused on the _applied_ and methodologies employed within community-based, participatory, and action-oriented research frameworks. Underlying the present review's overarching purpose and topical foci is the goal of informing IPV intervention and prevention approaches specifically relevant to, appropriate for, and inclusive of same-gender IPV perpetration among sexual minority women (SMW). However, while there is currently a burgeoning body of research related to the causes, correlates, and consequences of IPV within the context of women's same-gender relationships, the extensive literature database searches, described in a later section, conducted for the present review indicated that there is no currently available empirical research examining interventions implemented to address IPV within such contexts. As such, the systematic critical review provided here is structured according to two overarching research domains: (1) IPV interventions and prevention research and (2) IPV-related research specifically inclusive of sexual minority women but not necessarily restricted to IPV interventions or prevention efforts. The reviewed literature in both domains is restricted to research conducted within community-psychological and closely related research and practice frameworks.

In order to provide the contextual framing for the later-reviewed research literature, an overview of the social, political, and research climate within which the present review's substantive foci is situated is briefly presented below. This contextual overview is followed by details regarding the theoretical and methodological rationale for a critical methodological review of IPV intervention and prevention research specifically conducted within community-psychological and related fields. With these contexts and frameworks in mind, the methods employed for conducting the present systematic literature review are described in detail, followed by an integrative critical review of the empirical research obtained from the multiple systematic literature database searches conducted for this review.

# I. Background & Significance

Over the past several decades, there has been a considerable development of research and community action across the globe working to address intimate partner violence (IPV). In the United States, this research and activism stemmed primarily from first-and-second-wave feminist movements, which collectively led way to the U.S. Violence Against Women and, more specifically, the U.S. Domestic Violence Movement beginning around the 1980s. The public policies and community-based services specific to intimate partner violence resulting from this mainstream work continue to be almost exclusively focused on men's abuse toward women [e.g., @black2011national; @tjaden2000full]. Consequently, intimate partner violence occurring among members of the Lesbian, Gay, Bisexual, Transgender, and Queer (LGBTQ) population has been critically overlooked and the IPV-related needs of this population have gone unmet with severe consequences<!--**RS1.** NAME THESE CONSEQUENCES--> [@ristock2001decentering; @walters2013national]. Importantly, recent nation-level data indicate that LGBTQ individuals experience IPV at rates comparable to heterosexual individuals, and are in many ways at higher risk of experiencing violence than heterosexual population [@walters2013national].<!--**RS2.** NAME THESE WAYS OF INCREASED RISK--> Pertinent to this study, these data provide evidence that the prevalence of female same-sex intimate partner violence (FSSIPV) in particular occurs at much higher rates than expected by researchers conducting national-scale intimate partner violence survey work [@walters2013national]. This, along with historic data corroborating these statistics, suggests that the prevalence of FSSIPV has been grossly misrepresented throughout the U.S. Women's and Domestic Violence Movements. The causes and consequences of this misrepresentation lie in historical notions that regard female same-sex intimate partner violence as a phenomenon that is either non-existent [@cecere1986second], not possible [@hammond1989lesbian], or not worthy of consideration based on anti-LGBTQ ideological viewpoints [@durish2011documenting; @ristock2001decentering; @ristock2011intimate]. The relative lack of research on female same-sex IPV is characteristic of a long history of oppressions committed against sexual and gender minorities and traditional gender role stereotypic expectations of women to be nonviolent, or the notion that women do not possess the ability to be violent, or at least violent enough to inflict pain on others [@gilbert2002discourses; @girshick2002no; @hassouneh2008influence; @little2010perceptions].

In line with the heteronormative stereotypic notion of women's incapability of violence, FSSIPV-inclusive research to date has tended to fall into one or both of the following categories: (1) reports of the estimated national prevalence of FSSIPV; and/or (2) heterosexual groups' and individuals' gender role stereotypes about women's same-gender relationships, and the possibility of violence in those relationships<!-- **RS4.** REVISIT--> [e.g., @mcclennen2005domestic; @messinger2011invisible]. Compared to attention given to issues collectively faced by the LGBTQ population, the relatively large dedication of federal, state, and private funding for research related to violence against women and domestic violence since the original signing of the Violence Against Women Act (VAWA) has been almost exclusively used for developing services for presumed heterosexual, cis-gender, female survivors of abuse perpetrated by male intimate partners with similarly presumed heterosexual and cis-gender characteristics [@ristock2001decentering]. However, results of research related to IPV occurring within this narrowly defined population are not necessarily representative of the prevalence, causes, and correlates of IPV experienced by members of the LGBTQ population [@burke1999violence; @hassouneh2008influence; @ristock2001decentering]. Thus, domestic violence services that emerged out of the U.S. Women's and Domestic Violence movements of the 1980s and 1990s (e.g., emergency shelters for survivors and batterer intervention programs), which are largely based on this heterosexual-IPV-focused research, remain ill-equipped to serve LGBTQ IPV survivors, perpetrators, and their families [@hart1986lesbian; @lobel1986naming; @mclaughlin2001knowledge; @ristock2001decentering; @smith2011women].<!-- In recent years, however, researchers have begun to address the lack of empirical knowledge around the prevalence and causes of intimate partner violence among Lesbian, Gay, Bisexual, Trans, and Queer populations by adding distinctions of sexual orientation to existing national intimate partner violence inquiries and reports [@walters2013national]. -->

## Rationale

The above-described barriers to IPV-related research, intervention, and prevention efforts specific to sexual minority women necessitate a research approach that takes into account this unique context. Community psychological theory values the notion that the communities in which research is taking place and/or affecting (whether directly or indirectly) should be as involved as possible in all phases of the research process, rather than solely as anonymous data points in the analysis [@senn2005you; @maguire1987doing]. Community psychology thus favors inclusion over exclusion, participant voices equally with researchers' voices, and participatory and/or purposive sampling methods over convenience sampling methods [@balcazar2004participatory; @senn2005you; @maguire1987doing]. The literature reviewed here is evaluated and critiqued according to these types of community psychological standards regarding (1) _research methodologies_, (2) _data analytic approaches_, (3) _interpretations of findings_, and (4) _research dissemination_.

`r tufte::newthought("Research Questions (RQs)")`

> **RQ-1:** To what extent are community psychological theories and methodologies implemented, or not, in community psychology-based research related to intimate partner violence (IPV)?

> **RQ-2:** How has the implementation of community psychological research has evolved over time since the origination of the field, as well as potential trajectories based on the current state of discourse within community-psychology and closely related research and practice disciplines?

# II. Theoretical Grounding

The present systematic review is situated within an ecological framework and posits that individuals are both affecting and affected by their environmental settings [@espino2008spirit; @kelly1977social]. This review is further grounded in an action-oriented theoretical and methodological framework [@chandler2003transforming; @brydon-miller2003why; @friedman-nimz2006blending; @kelly2004community; @noffke1997professional; @prilleltensky2001value-based; @prilleltensky1997values; @seidman2012emerging], as well as social scientific theories related to IPV and sexual minority women [@meyer1995minority; @meyer2003prejudice; @meyer2015resilience]. These frameworks collectively incorporate the community-psychological concepts discussed below.

## Ecological systems theory and the Social Ecological Model

Ecological analysis provides a framework which observes, describes, and evaluates an individual's development, experiences, or behaviors in terms of the individual's ecology, or environment, and the transactional relationships among the individual and one or more structural levels comprising the ecological system [@bronfenbrenner1977toward; @centers2015social; @barker1964ecological; @sarason1972creation]. Ecological systems theory and the social ecological model are cornerstones for the field of Community Psychology, as this theoretical framework necessitates research that looks beyond an individual in order to better capture and analyze the complexities that both influence and are influenced by individuals [@lounsbury2009introduction]. Ecological analysis is especially important to the design, implementation, and evaluation of community-based interventions [@trickett2009community; @trickett2009multilevel; @trickett2011water; @lounsbury2009introduction], including IPV-focused interventions and prevention approaches [@centers2013taking; @centers2015social; @baker2013lessons].

## Protective (versus risk) Factors & Community Health Promotion

<!-- [@baral2013modified; @whitaker2014linking; @tharp2013systematic; @walton-moss2005risk; @heckert2004battered; @stokols1996translating] -->

## Community & Individual Empowerment

<!-- [@speer1995community; @riger1993what; @beeker1998community; @cobb1993empowerment; @collins2002black] -->

## The Action Research Cycle & Community-Based Participatory Action Research (CBPR)

<!-- [@fine2003participatory; @chandler2003transforming; @brydon-miller2003why; @friedman-nimz2006blending; @kelly2004community; @noffke1997professional; @prilleltensky2001value-based; @prilleltensky1997values; @seidman2012emerging; @anders1966action] -->

## Coordinated Community Response (CCR)

<!-- [@gondolf2007theoretical; @barner2011interventions; @dutton2007duluth] -->

## Minority Stress (MS) Theory & Resilience

<!-- [@meyer2003prejudice; @meyer2010right; @meyer1995minority; @meyer2015resilience] -->

## Specific Action-Oriented Research Methods

### Grounded Theory & Mixed-Methods Research

<!-- [@charmaz2006constructing; @corbin1990basics; @strauss1994grounded; @morgan2014mmr; @creswell2013research; @greene1989toward; @johnson2007toward] -->

### Program Evaluation

<!-- [@rossi2004evaluation; [@greene1989toward; @kidder1987qualitative; @mertens2012program; @owen1999program; @royse2009program] -->

## Intersecting Community-Psychology Theory & Research Methodology

The present critical methodological review examines the intersections that exist across the core theoretical and  methodological domains of community-psychology as a research field in terms of their applications and manifestations in various research settings. The action-oriented and values-transparent community psychological research approach was born out of a resistance to research methodologies, social policies, and implementation practices that ultimately served to reinforce and/or strengthen social and economic inequalities [@fine2003participatory; @senn2005you; @balcazar2004participatory]. This foundation necessitates vigilance in critical reflexivity throughout and beyond the research process. The critical literature review provided here is intended to serve this key characteristic of community psychology.

# III. Systematic Literature Review Methodology

## Literature search strategy

<!-- _B. Focal data bases_ -->

Six separate literature searches were conducted using the [_PsycINFO_](http://www.apa.org/pubs/databases/psycinfo/) and [_Web of Science_](http://wokinfo.com) online citation indexing databases via the [Portland State University library website](library.pdx.edu):

<!-- _C. Key search terms_ -->

1. _IPV, Domestic Violence, or Partner Abuse - General_
2. _IPV, Domestic Violence, or Partner Abuse Interventions_
3. _IPV, Domestic Violence, or Partner Abuse Intervention Evaluations_
4. _Female Same-Sex/Same-Gender IPV, Domestic Violence, or Partner Abuse - General_
5. _Female Same-Sex/Same-Gender IPV, Domestic Violence, or Partner Abuse Interventions_
6. _Female Same-Sex/Same-Gender IPV, Domestic Violence, or Partner Abuse Intervention Evaluations_

<!-- D. Inclusion/exclusion criteria -->

Because this review is not intended to provide a cross-national examination of IPV interventions research, each of the above literature searches was restricted to empirical studies conducted within the United States. In addition, to focus the review around a community psychological framework and intimate partner violence, results were initially confined to articles published in scholarly peer-reviewed journals specific to Community Psychology. The list Community Psychology journals included _The American Journal of Community Psychology_ and the additional publications, provided in Table 1, endorsed by the Society for Community Research and Action (SCRA) as related to Community Psychology [@scra2017other]. This restriction yielded a limited number of empirical articles specific to intimate partner violence interventions in general, and yielded zero (0) IPV intervention-related studies specifically inclusive of sexual minority women. Thus, the literature searches were revised to also include articles published in any of the following violence-specific publications: _Journal of Interpersonal Violence_, _Journal of Family Violence_, _Violence Against Women_, or _Violence and Victims_. These additional publications were included based on results from a database search of IPV-related terms conducted with no constraints imposed on the publishing journal, which revealed that these journal publish the majority of IPV-related research ($n_{articles} =$ `r pander(as.character(jv.n[, 1]))`, respectively), and (2) the alignment of the topical and methodological foci of these violence-related journals with community psychological principles and values. Finally, each database search was restricted to empirical studies published between 1965 and 2017 [i.e., the year of the [Swampscott conference](http://www.scra27.org/publications/tcp/tcp-past-issues/tcpsummer2014/remembering-swampscott/) and the present year; @fryer2008some].

Details regarding the number of results obtained from each of the above-listed database searches are provided in Table 2. Collectively, the literature database searches yielded `r n.init` journal articles, of which `r n.inits3` focused on intimate partner violence prevention and intervention programs, approaches, and evaluations, ; whereas the remaining `r n.inits4` consisted of research specific or closely related to IPV among sexual minority women and LGBTQ populations in general, but not necessarily specific to IPV prevention nor intervention among these populations. The majority of the latter research sub-category's initial results focused primarily on the prevalence of IPV among sexual minority populations, as well as causal antecedents, risk factors, correlates, and consequences of IPV among members of these target sub-populations.

Through a systematic evaluation of the full set of results obtained from the database searches, described below, a large number of the latter category's articles published in the included violence-specific journals were determined to be, at best, loosely relevant to the community-psychological focus of this review. Specifically, among the two empirical research articles returned from the database search seeking IPV interventions research specifically inclusive of sexual minority women [i.e., @witte2015perceived; @edelen2009measurement], one examined college students general attitudes about same-gender IPV, and another detailed an item-response theory approach to measuring teens' attitudes about dating violence among heterosexual adolescents. As such, results from the LGBTQ-IPV research sub-category were restricted to studies published within any of the community-psychology-related scholarly journals (see Table 1) in an effort to maintain the overall community-psychological focus of this review [@scra2017other]. The final set of `r nrow(MAP)` articles included in this review therefore consists of `r nrow(MAP[MAP$scat == "S3", ])` empirical studies related to IPV intervention and prevention program evaluations in general, and `r nrow(MAP[MAP$scat == "S4", ])` studies specific to sexual minority populations.

## Systematic Review Methodology

The selection of empirical literature, representing a community-psychology-focused subset of the U.S.-based IPV-related literature, was reviewed using a primarily deductive _qualitative comparative analytic approach_ [_QCA_, see Appendix B;  @leech2007array; @onwuegbuzie2017framework]. This review approach was conducted in two phases, each of which was primarily conducted using of the _`R` Statistical Programming Language and Environment_ [details regarding specific _`R`_ packages used in conducting analyses and presenting this review are provided in Appendix B; @R-base].

The first QCA phase served as the initial data reduction, organization, and quality-control process undertaken to determine the final set of articles to be included in the formal review. Each article in the full set of results ($N = 106$) from the previously-described literature database searches was first assessed according to the basic criteria for inclusion in the present review (i.e., U.S.-based empirical research). The content of each of the articles retained from this first filtering procedure was subsequently evaluated in terms of its overall relevance to the present review. Thus, any articles returned from the above-described database searches that either did not meet the basic inclusion criteria for this review or were determined to be unrelated to the topics of interest for the current review were excluded from the set of formally reviewed articles ($N_{excluded} = `r length(MAPrm)`\ $). The final set of `r nrow(MAP)` included studies is divided into two research domains: (1) IPV intervention evaluations research ($n = `r nrow(MAP[MAP$scat == "S3", ])`$), and (2) community-psychology-specific research specific to LGBTQ-IPV and inclusive of sexual minority women ($n_{c_{2}} = `r nrow(MAP[MAP$scat == "S4", ])`$).

The second QCA phase served as a systematic method for examining the similarities, differences, and anomalies among the final set of reviewed articles according to the above-described two categories determined in the first QCA phase data reduction and organization process [@onwuegbuzie2017framework; @onwuegbuzie2009qualitative]. That is, the reviewed literature was categorized according to the commonalities in overarching research topics, target populations, sampling frames, sampling and data collection methodologies and measures, data analytic approaches and procedures, findings, and implications.

# V. Integrative Literature Description and Review

As previously noted, the research reviewed here is conducted within a community-psychological or closely related research framework and thus represents a subset of the available IPV-related empirical literature. The majority of the below-reviewed literature specific to evaluating IPV perpetration interventions was published during or before 2008, whereas the subset of IPV-related research specifically inclusive of sexual minority women, reviewed in later sections, did not begin to emerge until 2005 (see Figure 1). Given this timeline and history, the review below provides details regarding the research methods and key findings from the set of earlier (i.e., published during or before 2008) evaluations of IPV perpetrator interventions. The first review is intended to provide an overview of the foundational research related to IPV interventions conducted within frameworks aligning with applied community-psychological theory and methods.

## IPV Perpetrator Intervention Program Evaluations

`r tufte::newthought("Brief History of U.S. IPV Perpetrator Interventions.")` Efforts to address violence against women and in particular intimate partner and sexual violence in the United States began with an overall focus on treatment and tertiary intervention approaches, which, understandably, were primarily focused on addressing the immediate needs of victims.<!-- CITE -->  Until IPV perpetration became a crime in all 50 states, these efforts were in large part initiated and sustained on "grassroots" levels, connecting with and building upon one another toward efforts to affect more large-scale changes at the policy and structural levels. The criminalization of IPV perpetration was eventually followed by the enactment and enforcement of mandatory arrest laws across the country, which, while varied in scope and levels of implementation, essentially require police officers responding to calls deemed characteristic of domestic violence impose some level of punitive action against the accused offender in the situation. These laws were created and continue to be enforced under the goal of ensuring victims' safety. The U.S. 1994 Violence Against Women Act shared a similarly victim-safety-centered purpose and, among a plethora of policy implications, was the first national-level policy providing at least a minimal amount of federal and state-level funding allocations specifically for developing and sustaining services for victims of IPV in each U.S. state.

During the same time period described above, work was also being done to address the issue of IPV perpetration, which ultimately led to the emergence of various programs and focused on tertiary and secondary levels of IPV prevention across the country [@tolman1995intervention]. Overarching approaches to IPV perpetrator interventions in the U.S. varied substantially throughout the late 1980s and through the early 2000s, and a majority of programs today have tend to follow a combination of approaches. For instance, cognitive behavioral therapy is often combined with the Duluth curriculum, which primarily targets intervention recipients' endorsement and internalization of patriarchal values of gaining and maintaining power and control over others [@price2009batterer; @pence1983duluth].

A common thread exists across the various approaches to IPV perpetrator interventions that is particularly relevant to the underlying purposes of the present review. As previously discussed, the IPV-related research foci of the late 1900s and early 2000s is beset aligned with the mainstream second-wave feminist movement in the U.S., as is the general focus of intervention and prevention efforts throughout the past several decades. As such, IPV perpetrator intervention approaches, such as the Duluth curriculum [@pence1983duluth] target heterosexual men's experiences, attitudes, and behaviors. Thus, while the underlying purpose of this review remains to inform IPV intervention and prevention efforts inclusive of sexual minority women, the available IPV interventions research, both within and outside of community-psychology and related disciplines, does not allow for any meaningful analysis of interventions with this specific population.

## Key Findings from Early Evaluations of IPV Perpetrator Intervention Programs

### Program Effectiveness

Using naturalistic observations of program practices and key informant (i.e., program participants' current romantic partners) reports of IPV perpetrators' reassault rates during the first over the course of 15 months following their initial intake into the intervention program, @gondolf1999comparison provides a foundational comparative evaluation of four IPV perpetrator intervention systems in four U.S. cities (i.e., Pittsburg, PA; Houston, TX; Dallas, TX; and Denver, CO). Findings from this study are, however, somewhat mixed in that comparisons to evaluate differences in reassault rates across the four study sites, representing a continuum of least-to-most comprehensive IPV perpetration intervention systems, showed few meaningful differences across intervention sites. Distinctions across the four sites are, however, more evident when individual perpetrator characteristics (e.g., psychopathology, substance abuse, previous arrests, etc.) and referral sources (e.g., court-mandated versus referral sources outside the court system) are also taken into account. Further, while there was no significant effect of intervention site on reassault rates, the effect of the most comprehensive intervention system among the four included in the study does tend toward significance, particularly when this site's effect is compared with the least comprehensive intervention system included in this evaluation.

Overall, the total recidivism rate observed across all four programs evaluated in @gondolf1999comparison\'s investigation ($n_{total} = 656$) was 32% <!-- (_n_ = 210) --> for physical abuse and 43-70% for non-physical abuse (i.e., controlling behaviors, 45%; verbal abuse, 70%; and threats, 43%). In addition, 72% <!-- (_n_ = 343) --> partner respondents reported that they "feel 'very safe'" and 66% <!-- (_n_ = 281) --> indicated that they were "'very unlikely' to be hit". However, only 12% <!-- (_n_ = 54) --> rated their overall quality of life following their partners' completion of the intervention as "better", another 12% rated their quality of life as "worse", while 22% <!-- (_n_ = 100) --> rated their quality of life as the "same" as it was prior to their partners' intervention participation (p. 53).

Despite these mixed findings, @gondolf1999comparison\'s, relatively, early investigation into the possible differential effects of IPV perpetrator intervention systems representing four distinct points along a continuum from least-to-most comprehensive systems informs questions regarding system-, dyadic-, and individual-level factors that may influence these systems' efficacy at reducing reassault among men who have perpetrated IPV toward one or more female intimate partners. In particular, @gondolf1999comparison\'s findings regarding differences across the four intervention systems were most informative to understanding the effectiveness of IPV perpetrator programs when multiple levels of analysis are considered. That is, the effects of intervention systems' characteristics (i.e., comprehensiveness of services and intervention program length) on reassault rates appears rather sensitive to the inclusion of system-level variables not specific to the IPV perpetrator intervention itself (e.g., referral sources) and dyadic- and individual-level variables (e.g., victim-perpetrator contact during the 15-month study period, perpetrators' IPV-related and non-IPV-related criminal backgrounds, perpetrators' substance use or abuse, etc.) in each analysis.

The primary data source for @gondolf1999comparison\'s study's outcome variables is key informant reports provided by participating IPV perpetrators' current romantic partners, regardless of whether those partners were the original victims leading to the men's intervention program participation. This sampling and data collection method is an interesting approach to evaluating IPV perpetrator interventions, and the use of key informant reports (e.g., victims', current and/or past romantic partners', and intervention program facilitators' perspectives used as primary or secondary reports of program participants' behavior) is somewhat thematic across a subset of subsequently-published literature included in this review<!-- EDIT --> [e.g., @gregory2002effects; @silvergleid2006batterer]. An additionally notable characteristic of @gondolf1999comparison\'s evaluation report is the transparency with which the study's results are presented. While the evaluation ultimately provided, at best, mixed support for more the effect of more comprehensive IPV perpetration intervention systems, the results are presented such a way that acknowledge the state of this specific practice's field, which, at the time of the study's publication, is possibly best characterized as disjointed and in need of a more concrete and consistent evidence-base.

In a separate effort to inform the question of IPV perpetrator intervention effectiveness from the victims'/survivors' perspectives, @gregory2002effects conducted in-depth one-on-one interviews with 33 women identified via police reports as having experienced IPV victimization perpetrated by men referred to a local IPV perpetrator intervention program in a rural Ohio county. Interview questions sought information regarding the offenders' behaviors before, during, and after their participation in the intervention. Regarding survivors' accounts of offenders' behaviors prior to being referred to the intervention, the authors found that many of the men entering the intervention had also been physically violent with past romantic partners, close relatives, and male friends. In addition, a substantial proportion of survivor respondents indicated that jealousy, substance abuse, and family-related issues (e.g., issues related to children, finances, household chores, etc.) were apparent causes of conflict leading to the perpetrators' use of violence. Survivors' also provided insights into their assessments of more underlying causes of abuse, including issues related to power and control, their partners' low self-esteem, and conflict related to sexual/intimacy issues and the perpetrators' infidelity in the relationship. Regarding program participants' partners' accounts of the intervention's effectiveness, the majority of the 33 respondents in @gregory2002effects\'s evaluation indicated either a decrease or complete elimination of violence in their relationships, while a third of the partners reported that the intervention program in fact became a new source of conflict in their relationship, and 19% reported abuse during or following the offenders' program completion.

A particularly notable descriptive finding from @gregory2002effects\'s investigation is that, on average, over seven years lapsed between the first occurrence of IPV in the relationships accounted for by the study's survivor respondents and the IPV incident resulting in the perpetrators' referrals to the intervention program. Although not explicitly connected in the study's findings report nor discussion, this finding may inform survivor respondents' apparent consensus that jail time should be an immediate and/or unconditional sanction imposed against individuals found guilty and/or under investigation for IPV perpetration. Further, an average time-lapse of this magnitude indicates a potentially critical flaw in the implantation of any form of a coordinated community response to IPV [@hart1995coordinated].

@gregory2002effects\'s evaluation is restricted to female survivors' accounts of male IPV perpetrators court-mandated, either as part of post-sentencing probationary requirements or deferred-sentencing conditions, to complete the intervention, and therefore does not include accounts of the intervention programs' participants who are not referred to the program by the courts. @gregory2002effects\'s sample further excludes accounts of same-gender IPV perpetration or victimization, as well as IPV perpetrated by female-identified individuals toward male-identified partners. This sampling frame is similar to that defined in @gondolf1999comparison\'s investigation (summarized above) both in terms of the specific included and excluded populations, as well as the fact that the sampling restrictions in both studies are, at least to some degree, a function of the populations served by the study sites themselves. That is, at the time the studies were conducted, the intervention programs evaluated in both investigations provided IPV perpetrator intervention services only to male-identified individuals who perpetrated IPV toward female-identified partners.

@hendricks2006recidivism conducted a comparative evaluation of two IPV perpetrator intervention programs in a small metropolitan Wisconsin county [@ingram2012nchs]. Although @hendricks2006recidivism ultimately describes the programs evaluated their investigation as two independent interventions, one of the programs, _"Reasoning & Rehabilitation (R&R)"_ is in fact evaluated as a sort of nested or secondary intervention within the county's larger IPV perpetrator intervention system, _"Stopping Abuse for Everyone (SAFE)"_ (p. 704). That is, individuals are referred to the _R&R_ program if they are determined as in need of greater levels of supervision based on a clinical assessment administered during the _SAFE_ program's intake process. Such individuals are expected to return to and complete the _SAFE_ program's intervention after completing the additional _R&R_ program. @hendricks2006recidivism\'s investigation also included an evaluation of the predictive validity of the _Level of Service Inventory–Revised_ [_LSI-R_; @andrews1994level], which is the assessment administered to determine intervention participants' levels of risk and need at intake for the _SAFE_ program. Regarding the latter, results from logistic regression analyses provided minimal support for the LSI-R scale's accuracy, sensitivity, and specificity in correctly classifying recidivating intervention participants (overall classification accuracy = 66% correct). However, while formal logistic regression analysis was not similarly conducted to examine the measure's predictive accuracy regarding program placement, comparisons via cross-tabulations and chi-square ($\chi^{2}$) analyses revealed significant differences in both LSI-R scores and recidivism rates among intervention participants. Specifically, participants who completed the _SAFE_ program without referral to the _R&R_ program (14.4% recidivated) had significantly lower recidivism rates than those who completed both interventions (32.4% recidivated; $\chi^{2}(1) = 6.26,~p < .05$). As @hendricks2006recidivism note, because participants were referred to the _R&R_ program on the basis of their LSI-R scores, these differences in recidivism rates do not necessarily inform comparisons regarding each intervention program's individual effectiveness at reducing or preventing future violence perpetration among participants. However, a possibly missing point in @hendricks2006recidivism\'s report and analytic conclusions is that these observed differences may provide support for the discriminant validity of the LSI-R as a measure effective in determining the relative risk and needs levels of IPV perpetration intervention participants.

In general, research on the effectiveness of IPV perpetrator intervention programs in the late 1990s and early 2000s, including the above-reviewed research, provides a mixture of evidence in favor and not in favor of these programs' effectiveness [@feder2005meta]. The above-reviewed subset of the IPV-related literature reiterates the general ambiguity regarding effective approaches to IPV interventions [@gelles2001standards; @dutton2006transforming; @gondolf2007theoretical; @dutton2007duluth]. Unfortunately, this ambiguity has persisted, as is evidenced by the continued mixed findings presented throughout the overall body of IPV-interventions-related literature [@eckhardt2013effectiveness; @arias2013batterer; @babcock2016domestic]. This ambiguity has often been interpreted over the years as an ultimately adverse outcome such that the overall efficacy of IPV perpetrator interventions to prevent program participants' future IPV perpetration remains, at best, in question, and in some views non-existent [@dutton2006transforming; @dutton2007duluth]. However, such conclusions neglect attention to the full extent of the available evidence. It is crucial to consider that these interventions are in fact quite varied in terms of the underlying program theories, overall program structures, treatment modalities, and implementation [@gelles2001standards]. Further, the empirical community-psychology related literature reviewed above does provide some evidence that certain approaches to and components of IPV perpetrator interventions may be more effective than others [e.g., @gondolf1999comparison; @hendricks2006recidivism].

### Processes of Change

It is, therefore, important to explore the processes underlying successful outcomes (e.g., reduced or eliminated recidivism among participants) in these interventions. @silvergleid2006batterer provide one such exploration of the key processes facilitating positive change among men who successfully completed an IPV perpetrator intervention program in Portland, Oregon. @silvergleid2006batterer conducted in-depth, semi-structured, one-on-one interviews with ten intervention group facilitators and nine men who were within two-weeks of having completed their participation in the intervention and who were nominated by group facilitators. Four levels of change processes were identified through inductive thematic analysis of the interview data: (1) "community and extratherapeutic influences", (2) "organizational influences", (3) "group processes", and (4) "individual psychological development" (p. 144). The group-level processes seem especially influential in terms of facilitating a _process_ of change, in that this level of influence is further categorized into three sub-processes that appear to build from one another: (1) balancing support and confrontation, (2) sharing and hearing stories, and (3) modeling and mentoring. Facilitators' accounts further emphasized the group-level influences as instrumental in the process underlying intervention participants' "'resocialization' into a new manhood" [@silvergleid2006batterer, p. 151].

@contrino2007compliance quantitatively examined intervention program participants' levels of compliance with program requirements (e.g., attendance, engagement with the program, maintaining sobriety, nonviolence, etc.) and the extent to which participants retain key components of the intervention's content (e.g., power and control dynamics versus non-controlling behaviors). This investigation's focus aligns with @silvergleid2006batterer\'s qualitative findings regarding key influences underlying and facilitating IPV perpetrator intervention program participants' change processes. Specifically, both program participant and facilitator interviewees in @silvergleid2006batterer\'s sample emphasized the importance of learning new skills (e.g., taking a 'time-out') and engagement with program activities (e.g., reading required texts, journaling, acknowledging their past violent behaviors and the impact of those behaviors on others, etc.) in the change processes experienced by program participants:

> "The most emphasized aspect of awareness was the participant’s new understanding of the effects of their abuse on others. For many men, truly sit- ting with that understanding, the devastating impact of their actions on those around them, was a strong impetus for change" (@silvergleid2006batterer, p. 153).

Findings from @contrino2007compliance\'s process evaluation somewhat reiterate the above-described processes and corresponding outcomes among intervention participants. For instance, @contrino2007compliance examined the differential effects of intervention participants' levels of compliance (high versus low) with program expectation domains on the extent of participants' intake and internalization of the intervention, operationalized in @contrino2007compliance\'s analysis as recall of key components of the intervention's content (e.g., forms power and control). Participants' recall of power and control forms was found to vary as a function of four out of the ten assessed program expectation domains including (1) using techniques to avoid violence, (2) process-consciousness and communication skills, (3) self-disclosure<!-- of ones's feelings--> and non-defensiveness, and (4) use of respectful or sensitive language. However, domains including participants' sustained sobriety and nonviolence throughout their enrollment in the intervention, help-seeking, consistent program attendance, and active engagement in group sessions were not associated with the number of forms of power and control they were able to recall. The lack of effect of the latter two domains (i.e., program attendance and active engagement with the program) on participants' recall of intervention content is particularly interesting in light of the four domains for which such an effect was evident.

At a conceptual level, the above-listed four program expectation domains shown to influence intervention intake and internalization, appear thematically grouped as representing processes of change via internalization and application of the intervention. It seems logical that such change processes would coincide with being both physically and mentally present during the intervention itself. That no relationship was found among the attendance and engagement program expectation domains and participants' intake and internalization of the intervention is contradictory to these conceptual themes. The measure used to assess program expectation compliance is described in @contrino2007compliance\'s report as an adaptation of Edward Gondolf's "discharge criteria" [@contrino2007compliance, p. 1559]. The description provides limited information beyond the list of program expectation domains assessed, description of the 5-point likert-type response scale, and brief scoring information. Unfortunately, no sample items are provided for the original discharge criteria nor the adapted measure used in @contrino2007compliance\'s investigation, and the web address provided in the citation for Gondolf's original discharge criteria^[http://www.mincava.umn.edu/papers/gondolf/discharg.htm] does not appear to provide the original measure itself nor additional information regarding the measure's content. However, Gondolf's "discharge criteria" measure is provided by @gondolf2009clinician, along with details regarding its development, content, and usage with reference to its use in @contrino2007compliance\'s investigation. The _Discharge Criteria Form_ as published in @gondolf2009clinician is provided in Appendix C. The measure assesses intervention participants' level of compliance with the previously mentioned program expectation domains via a single question per domain. This structure limits the assessment tool in terms of its ability to capture the range of qualities and behaviors it is intended to measure. For instance, the item assessing the active engagement domain is written in such a way that, most likely, could only reliably capture explicit behavioral displays of engagement, thereby potentially omitting information regarding active engagement among participants whose expressions of engagement in the program may be less extraverted or more introspective. This limitation may help explain the above-described conceptual discrepancies apparent in @contrino2007compliance\'s findings. The measure itself could be improved in terms of its general applicability and sensitivity to the diversities that may exist among IPV intervention participants adding additional items assessing varying forms of the target behaviors for each of the assessed domains.

## Summary of Foundational IPV Perpetrator Interventions Research

The above-described IPV perpetrator intervention evaluation studies [i.e., @gondolf1999comparison; @hendricks2006recidivism; @gregory2002effects; @silvergleid2006batterer; @contrino2007compliance] was published in either the _Journal of Interpersonal Violence_ or _Violence Against Women_. Each of these evaluations focuses on IPV perpetrator interventions best characterized at the tertiary level of intervention and prevention such that the overarching target population in each evaluated intervention program is comprised entirely of individuals who have perpetrated IPV at least once in their lifetimes and the primary purpose each intervention program is to prevent these individuals' future IPV perpetration. Importantly, each programs' target treatment population is restricted to adult men who have perpetrated IPV toward a female-identified intimate partner.

Interestingly, @price2009batterer\'s findings from a national survey of 276 IPV perpetrator intervention programs ($N = 45$ U.S. states represented in the sample) suggest that, although the vast majority of these intervention programs serve a ratio of male-identified to female-identified IPV perpetrators is 9:1, $74%$ of respondents to @price2009batterer\'s survey indicated that they do offer programming for non-male-identified perpetrators, and 78% offer programming for homosexual IPV perpetrators. Thus, the target population restrictions of the IPV intervention programs evaluated in the above-reviewed literature may not be representative of the typical target population restrictions across the U.S., but are nonetheless representative of the typical recipients of IPV perpetrator interventions across the country.

```{r setup_Va, echo=FALSE, results='hide', fig.keep='none', fig.show='none', message=FALSE, warning=FALSE, cache=FALSE}
rm(list = ls())
source("bibs_cp.R")
knitr::opts_chunk$set(echo = FALSE)
panderOptions("p.wrap", "")
panderOptions("p.sep", "; ")
panderOptions("p.copula", "; ")
```

# Methodological Review of Community-Psychology IPV Interventions Research

The previously reviewed literature represents a subset of the foundational IPV perpetrator interventions literature, as the reviewed studies were specifically selected from the larger body of IPV literature based on (a) their general relevance to the substantive research focus of the present review (i.e., IPV interventions), and (b) their alignment with applied community-psychological theory and methods. The remainder of this review, however, will focus specifically on empirical research conducted within disciplines specifically related to community-psychology. Specifically, a methodological critical review of the community-psychology-focused IPV interventions literature is provided in the sections that follow, with a particular focus on the relevance to and implications for IPV intervention and prevention efforts inclusive of sexual minority women [`r paste0("@", MAP$bibkey) %>% pander()`].

## Publication Years

Although the previously-described database searches allowed for any research published between 1965 and the current year (2017), the earliest publication date in the literature reviewed here is `r min(MAP$year)`. This timespan is somewhat aligned with the previously-discussed political and legislative history of U.S. domestic violence policy and social movement(s). For instance, the original Violence Against Women Act (VAWA), which imposed provisions to actually enforce the illegality of family violence perpetration and gave way to more funding allocations for IPV-related research across multiple scientific disciplines, was passed in 1994, [@biden2014twenty; @modi2014role; @fine1998violence; @legates2001their, Ch. 3]. The two-fold implications of the legislative passing of the 1994 VAWA is of particular import to the present review, as the combination of (a) acknowledgement of IPV as a public health issue and (b) widespread government attention and funding being directed toward addressing IPV across multiple levels of analysis and disciplines could provide a nearly ideal landscape for conducting and cultivating innovative community-based action-oriented research.<!--TODO: CITE (esp. CP theoretical citations)-->

## Specific Research Topics

The overarching research topics across the community-psychological empirical literature reviewed here span individual, organizational, community, and structural levels of analysis. Specific topics at the community and structural levels of analysis include (1) development, improvement, and/or evaluations of coordinated community responses to IPV, (2) communities' capacities to address IPV, (3) and public policy related to IPV. Organizational level topics include (1) evaluation of IPV perpetration and/or victimization intervention or prevention programs, (2) evaluation of intervention program policies, and (3) interventions implemented in Non-IPV specific community-based service provider settings (e.g., hospitals). At the individual level, the majority of the reviewed SMW-inclusive research focuses on individual risk factors for IPV victimization and/or perpetration. Additional individual level topics include investigations of perspectives about or perceptions of IPV among individuals with no history of IPV or who are not a part of an intervention's or research investigation's target population, help-seeking behaviors among IPV victims, and consequences of IPV for individual victims or perpetrators.

## Methodological Critique

Three of the reviewed studies published in community-psychology-related journals focus on some type of IPV intervention program evaluation, two of which [@boal2014impact; @foshee2004assessing] are specific to IPV perpetrator interventions, whereas the remaining intervention-focused investigation [@thompson2000identification] evaluates an IPV victimization-focused intervention. Despite the relatively small number of IPV intervention evaluation studies published in community-psychology-related journals, these investigations collectively cover a range levels of analysis and intervention, settings, and evaluation methods. @thompson2000identification evaluated the efficacy of an intervention implemented in a primary healthcare setting designed to improve healthcare providers' and support staff's identification of IPV among patients and the level and quality of care provided to patients identified as IPV victims. @foshee2004assessing, on the other hand, implemented a multi-site, multi-wave intervention, the _"Safe Dates Project"_, targeting 8^th^-grade (at baseline) adolescents enrolled in ten public schools in North Carolina. The Safe Dates program was designed as a secondary teen dating violence prevention intervention, and comprised a 10-session treatment curriculum, a student-performed theatre production, a treatment booster in the form of an 11-page newsletter mailed to intervention recipients' homes three years after the initial treatment, and a telephone follow-up from a health educator shortly after the booster was mailed. It is somewhat difficult to evaluate the implementation and evaluation of the Safe Dates program using only information provided in @foshee2004assessing\'s relatively brief report. This is troublesome primarily because the treatment booster was found to be associated with _increased_ post-intervention psychological abuse perpetration among adolescents with high baseline psychological abuse scores. Details regarding the content of the booster are not available in the report, most likely due to space restrictions imposed by the publishing journal (_American Journal of Public Health_), which may provide better insight regarding the possible mechanisms by which the treatment booster caused increases in violence perpetration.

Finally, @boal2014impact provide evaluated the implementation of legislative policies guiding IPV perpetrator intervention program practices. This particular investigation mirrors the earlier IPV perpetrator interventions literature published in violence-specific journals reviewed in the previous section in that the authors' evaluation spanned multiple levels of analysis (i.e., structural/policy- and organizational). The overarching research design employed in @boal2014impact\'s longitudinal investigation of the implementation of standards for IPV perpetrator programs reflects a careful examination of the multiple factors influencing these programs' overall and day-to-day practices. However, similar to the earlier perpetrator interventions literature, @boal2014impact's analysis is bound by the limits of the policy and programs under evaluation, as is reflected in the evaluated policy's focus on program practices as they relate to intervention with male-identified individuals who have perpetrated abuse toward female-identified intimate partners.

```{r resetup, echo=FALSE, results='hide', message=FALSE, warning=FALSE, cache=FALSE}
panderOptions("p.wrap", "_")
panderOptions("p.sep", ", ")
panderOptions("p.copula", ", and ")
```

# VI. Integrative Literature Critique

Research conducted within the subset of community psychology focused around intimate partner violence was initially evaluated according to the level of inclusion and exclusion of the historically marginalized population of particular interest for the purposes of this review: sexual minority women (SMW). The implementation of action-oriented community-psychology methodologies and analytic approaches was then reviewed within each of these categories (i.e., inclusion or exclusion of SMW) in terms of (1) the appropriateness of the methods to the research question(s), (2) how the methods facilitated the inclusion or exclusion of sexual minority women, and (3) whether and how (where applicable) exclusion of sexual minority women is justified.

## Methodological Rigor

The notion of "scientific rigor" is particularly important in evaluating a set of applied social science research studies employing varying methodologies. This is because "rigor" is not necessarily clearly defined across methodologies, and some research philosophies do not consider certain methodologies as capable of achieving scientific rigor at all. For the purposes of this review, methodological rigor is broadly defined as the extent to which a given study employs research methods that best address the overarching research question(s) and/or hypothesis/hypotheses, and the quality of the implementation of those methods. This definition of methodological rigor therefore does not prioritize a particular method nor category of methods (e.g., quantitative over qualitative, mixed-methods over single-methods, etc.), but rather prioritizes the choice and implementation of methods employed to address a given study's purposes. In addition, this definition of methodological rigor allows for more specific and in-depth consideration of the limitations presented, and not presented, in each study's report.

Rigor in action-oriented community-based research methods was evaluated according to the choice, description, justification, appropriateness, and execution of each reviewed study's design (i.e., experimental or cross-sectional) and overarching methodology (i.e., quantitative, qualitative, or mixed-methods). Each of these aspects of the reviewed literature was identified in terms of each evaluated study's purpose, hypotheses, and/or research questions description, sampling frame definition, sampling and data collection methods, analytic approach(es), and description of findings and limitations. Because the underlying goals of this systematic review are motivated by the continued relative absence of sexual minority women in the larger body of IPV-related empirical research literature, especially in terms of IPV perpetrator interventions research, particular attention was given to the sampling frame definitions and sampling methods employed among the empirical studies reviewed here. That is, the evaluated research included in the present review was specifically evaluated in terms of how the methods facilitate the inclusion or exclusion of specific populations, particularly sexual minority women, and whether and how the exclusion of specific populations is justified in each empirical study's report.

In addition, to assess transparency and reproducibility of the research methods and findings, the overall presentation, dissemination mechanism(s), application, and accessibility of the research was noted where available or applicable. These latter assessments of research transparency and reproducibility also incorporated considerations regarding the incorporation of key and/or distal stakeholders' input. The accessibility of the research to primary and distal stakeholders would be reflected according to whether and how stakeholders are provided information about and access to reports of a given project's progress and findings. The role of stakeholder input in the evaluated community-psychology literature was noted in terms of the extent to which efforts made to ensure that _all available_ stakeholders' and informants' voices are considered throughout the research process, and that certain voices are not unjustifiably privileged over others. These considerations include evaluation of whether feedback is explicitly solicited, or at least accepted when offered, from key stakeholders and informants to the research, and whether such feedback is genuinely considered by the primary researchers of a given investigation.

## Methodologies & Methods Utilized

The majority of the reviewed studies follow quantitatively-based methodologies ($n = 7; 64%$), whereas only two of the reviewed community-psychology-specific studies employed qualitative methodological approaches, and another two utilized mixed-methodological approaches. Of the reviewed quantitatively-based studies, $36%$ ($n = 4$) employed experimental, rather than cross-sectional, designs, of which three followed a longitudinal experimental design (defined for this review as including three or more data collection time-points) and one used a pre-/post-test design (i.e., two data collection time-points). All of the seven quantitatively-based studies used self-report survey measures as the primary datasource. The two qualitatively-based studies collected data using one-on-one interviews. Finally, among the two studies following mixed-methodological designs, one study administered and analyzed data from a self-report survey comprised of open-ended and closed-ended questions ($n = 1$), whereas the second mixed-methods study employed a multi-method approach by collecting data using a combination of closed-ended self-report survey questions, one-on-one interviews, and a focus group.

## Sampling Frame Definitions and Sampling Methods

As previously mentioned, the sampling frame definitions among IPV the reviewed literature specific to IPV perpetrator interventions is almost universally restricted to heterosexual male-identified individuals who have perpetrated IPV. The exception to this overarching trend is @foshee2004assessing\'s randomized control trial evaluation of the Safe Dates program among adolescents, in which the sampling frame was defined according to geography, age, and school type (i.e., 8^th^ grade students enrolled in a selection of public schools located in multiple North Carolina counties).

In general, research related to interventions for which the target population is IPV victims, potential victims, or survivors follows a similar trend, but in the opposing direction, such that the majority of such studies' sampling frames are typically restricted to female-identified individuals who have experienced or who are at risk of experiencing IPV victimization. However, the present review systematically sought out the subset of community-psychology-related IPV research specifically inclusive of sexual minority women. The database searches described earlier in this paper, yielded seven empirical research studies published within community-psychology-related disciplines in which sexual minority women were specifically included in the sampling frame definitions [@blosnich2009comparisons; @balsam2005relationship; @edwards2016college; @glass2008risk; @lewis2014sexual; @oswald2010lesbian; @sylaska2015disclosure], all of which included sexual minority women with histories of IPV victimization. Three of the latter-described studies also included women who had perpetrated IPV toward a same-gender romantic partner [@balsam2005relationship; @glass2008risk; @lewis2014sexual]. The sampling frame definitions for three of the reviewed SMW-inclusive research studies also included sexual minorities identifying as male, transgender, and/or gender-queer [@sylaska2015disclosure; @edwards2016college]. Finally, two studies included heterosexual men and women, in addition to sexual minority women, in their sampling frame definitions [@edwards2016college; @blosnich2009comparisons].

# Strengths, Weaknesses, and Implications of the Reviewed Literature

The multi-part systematic review presented here provides a unique perspective of IPV-related empirical research by restricting the reviewed literature as a whole to only include studies published either in violence-specific journals determined by the primary author as well-aligned with community-psychological or in journals endorsed by the Society for Community Research and Action as closely aligned with or related to community-psychology values, theory, and methods. This perspective therefore inherently incorporates applied research conducted within a range of action-oriented, community-based, participatory, and multilevel frameworks.

Overall, key community-psychological values, theory, and methods are evident throughout the above-reviewed IPV-related literature conducted within community-psychology-specific disciplines and related research frameworks. The implementation of those values, theory, and methods is also generally well-carried out with many research reports incorporating reflexivity regarding various design and methodological considerations throughout the research process.

Some interesting concerns do arise, however, in terms of the implementation of community-psychological principles related to stakeholder input and intervention settings. Empirical research wherein the sampling frame and level of analysis is defined as either the intervention setting itself or intervention program staff/volunteers is an inherently community-based participatory evaluation method well suited for research conducted within an action-research cycle framework [@fine2003participatory; @kelly2004community]. However, in reviewing above-described literature, it became increasingly evident that community-based participatory evaluation methods may hinder the action component of an action-research cycle. Results from the the earlier-described literature database searches indicated that _no_ empirical research study exists that evaluates on any level (i.e., from formative and descriptive to assessing processes and outcomes) IPV interventions specifically inclusive of sexual minority women. This conclusion relates to research conducted both within and outside of community-psychology and related disciplines. The available community-psychology-related research literature specific to IPV interventions remains instead almost exclusively focused on IPV occurring among heterosexual couples, and particularly IPV perpetrated by male-identified individuals. Evaluation of the above-reviewed literature indicates that this restriction is often described as primarily a function of the existing structure and practices of the interventions' settings. Thus, it seems that the implementation of certain principles of community-based participatory evaluation methods may in fact constitute a major barrier to conducting action-oriented research. One potential path toward re-starting a stalled action-research cycle such as that described here is to more actively respond to and address limitations existing within a given intervention setting before, during, and especially following the conclusion of research activities within an intervention setting.

# Reflections on the Process of Writing this Review

At multiple junctures in the development of this review questions and suggestions along the lines of "Why not broaden the scope to include sexual minority _men_", or "perhaps remove the focal population restriction from the review's scope altogether". The present review was, in a sense, deliberately poised by the author to potentially fail in finding an adequate body of literature covering the present review's primary substantive research topic. That is, having spent several years researching IPV-related topics specific to sexual minority women within community-psychology-specific frameworks, the author was quite aware of the overall dearth of empirical research conducted on this specific topic that is specific to the author's population of interest. The rationale and justification for attempting to conduct a systematic review of a body of literature that most likely, and in fact, does not exist lies in the author's desire to better understand _why_ the particular subject of women's use of violence in their same-gender romantic relationships remains a consistently lacking area of research. This is particularly justified in light of the long awaited-for validation of what was likely already known by a majority of members of the sexual minority women community, in general, which is that IPV does in fact exist among us and in our community. It can be a bit of a tough pill to swallow, so to speak, but is nonetheless, in the author's experience, a typically known fact within SMW communities that IPV is perpetrated and experienced among our community members as much as, if not more than, it is among our brothers in the sexual minority male communities, as well as among heterosexual communities. The silence around the topic of IPV perpetrated by sexual minority women, however, is what most intrigues this researcher. What facilitates this silence? It is a fallacy to assume the silence is maintained primarily by the community itself, as researchers within or closely tied to the SMW community, such as Claire Renzetti [@renzetti1992violent], Janice Ristock [@ristock2002no], and Ruthann Robson [@robson1990lavender], have published, relatively, extensively on the subject over the past few decades. Yet it remains that _no_ empirical research regarding IPV intervention nor prevention approaches appropriate for, relevant to, nor specifically inclusive of sexual minority women has been conducted by the very research field found on principles of diversity and innovation in research methodologies [i.e., Community-Psychology; @fine2003participatory; @balcazar2004participatory; @maguire1987doing].

# References
