---
title: "Literature Search Methods<hr class=\"SemiBold\" /><figure class=\"title\"><img src=\"graphics/inputs/flowchart.png\" alt=\"Flow-chart of systematic literature database search results and decisions for inclusion and exclusion in formal review\" width=\"50%\"></figure>"
fignos-plus-name: "Figure "
tablenos-plus-name: "Table "
---

<span class="marginnote" style="font-style:italic;margin-top:-5em;">Flow-chart of systematic literature database search results and decisions for inclusion and exclusion in formal review"</span>

```{r setup, echo=FALSE, results='hide', message=FALSE, warning=FALSE, cache=FALSE, fig.show='none', fig.keep='none'}
setwd("../")
source("bibs.R")
source("cdbk.R")
setwd("docs")
knitr::opts_chunk$set(echo=FALSE)
```

<hr class="Bold" />

Six separate literature searches were conducted using the PsycINFO (PI) and Web of Science (WoS) online citation indexing databases via the Portland State University library website:

1\. _**IPV - General**_
    2\. _IPV Interventions_
    3\. _IPV Intervention Evaluations_
4\. _**Female Same-Sex/Same-Gender IPV (FSSIPV) - General**_
    5\. _FSSIPV Interventions_
    6\. _FSSIPV Intervention Evaluations_

Because this review is not intended to provide a cross-national examination of IPV interventions research, I restricted each of the above literature searches to empirical studies conducted within the United States and published between 1965 and 2017 [i.e., the year of the [Swampscott conference](http://www.scra27.org/publications/tcp/tcp-past-issues/tcpsummer2014/remembering-swampscott/) and the present year; @fryer2008some]. In addition, to focus the review around community psychology theoretical and methodological frameworks, I initially confined the search results to articles published in scholarly peer-reviewed journals specific to Community Psychology. The list of Community Psychology journals, provided in {+@tbl:jcp}, included _The American Journal of Community Psychology_ and additional publications endorsed by the _Society for Community Research and Action (SCRA)_ as closely related to community psychological research [@scra2017other]. This restriction yielded a limited number of empirical articles specific to intimate partner violence interventions in general, and yielded zero (0) IPV intervention-related studies specifically inclusive of sexual minority women. In response to this initial finding, I re-ran the first database search listed above (labeled as _"IPV - General"_) using the same keywords, publication year range, and location restrictions as before, but omitting the previously-imposed constraints on the journal title parameter. Then, taking advantage of of the various data points provided along with the primary sources returned from a given search in the both PsycINFO and Web of Science databases, I extracted tabulated data comprised of the journal title of each article in the results list and the total number of articles returned from each of those journals for the latter database search's results.

<!-- Evaluation of these data yielded a shortlist of potential journals to additionally include in the list of publication titles specified in each of database searches listed above.  -->

Based on (a) the volume of IPV-related literature published by each journal and (b) the alignment of the topical and methodological foci with community psychological principles and values, I selected the following four violence-related journals to be added to the list of specified publications in the database searches: (1) _Journal of Interpersonal Violence_, (2) _Journal of Family Violence_, (3) _Violence Against Women_, and (4) _Violence and Victims_. I then re-ran each of the six database searches with the publication title parameter restricted to any of the community-psychology-specific journal titles listed in {+@tbl:jcp} or any of these four violence-specific publications (see {+@tbl:jv}).

```{r dbsrchkable}
## BELOW IS FOR .DOCX/.HTML OUTPUT ##
dbsrch[, 2] <- sapply(dbsrch[, 2], Rretex, op = 2, USE.NAMES = F)
dbsrch[, 2] <- gsub("\\\\textsc\\{(.*?)}", "**\\1**", dbsrch[, 2])
dbsrch[, 3] <- sapply(dbsrch[, 3], Rretex, op = 2, USE.NAMES = F)
dbsrch[, 3] <- gsub("\\\\footnotesize\\{(.*?)\\}", "\\1", dbsrch[, 3])
names(dbsrch) <- c("", "Database Search[note]", "$Range_{N_{Results}}$")
library(kableExtra)
kable(dbsrch, caption = "Descriptions of database searches conducted with corresponding ranges of the number of results returned {#tbl:dbsrch}", align = c("r", "l", "l")) %>%
    add_footnote("For each database search, multiple search terms were included for the subject/keywords parameters to represent intimate partner violence<br /><br />", threeparttable = TRUE)
```

Collectively, the six database searches yielded `r n.init` journal articles after removing duplicates (see {+@tbl:dbsrch}). This selection of empirical research constitutes a community-psychology-focused subset of the available U.S.-based IPV-related literature. Among the initial set of `r n.init` articles, `r Riley::Rperc(n.inits3, n.init)` (`r n.inits3`) present IPV-related research focused on intervention and/or prevention approaches, programs, and evaluations; however, the majority of this research is not inclusive of sexual minority women. Conversely, the remaining `r n.inits4` articles consist of IPV-related research specifically inclusive of sexual minority women; however, does not directly concern IPV intervention or prevention approaches. Rather, this latter category of research primarily focuses on the prevalence, causal antecedents, risk factors, correlates, and/or consequences of IPV among sexual minority women and LGBTQ populations in general.

-----

# Analytic Approach

The six database searches were intentionally designed to successively narrow the search results from IPV-related research in general (regardless of focal population(s)) to IPV-related intervention and/or prevention research specific to sexual minority women. Correspondingly, the literature obtained from these database searches was reviewed through a deductive analytic procedure conducted in two phases: (1) initial screening, assessment, and data organization to determine which articles to include in the formal review; and (2) systematic review and methodological evaluation of the literature retained from the first analytic phase of the literature. Both analytic phases were acheived using the _`R` Statistical Programming Language and Environment_, the _`RQDA`_ and `RSQLite` _`R`_ packages, and relational databases built and managed using `Structured Query Language` [`SQL`; details regarding specific _`R`_ packages used in conducting analyses and presenting this review are provided in _Appendix B_; @R-base].

## Initial Literature Screening, Assessment, \& Organization

Each of the `r n.init` articles returned from the database searches was assessed according to three successive levels of inclusion criteria. The first and most basic inclusion criterion is that the articles must present U.S.-based empirical research. Second, the content of each article should be directly applicable to intimate partner violence interventions (e.g., intervention program development, implementation, and evaluation research; applied community-based research methods; etc.). To assess the second criterion, I coded each article using keywords from the authors' description of substantive research topics covered. This information was obtained by first examining each article's title and, if available, abstract or keywords list; and then reviewing the stated purposes, research questions, or hypotheses provided in the main body of each article. The latter step was done to ensure that the coding of each article's focal resarch topics was both accurate and comprehensive, as this coding was subsequently used as a "filter" for excluding articles not relevant to IPV interventions. Specifically, I examined the list of codes generated from this process (see codes listed under the "_Research Topic_" category in {+@tbl:cdbk}) and selected the following codes that fit within the scope of this review's previously-described goals and research questions:

`r pander(as.list(tpFilterdf$clab))`

Finally, a particularly crucial inclusion criteria for literature obtained from the fourth through sixth database searches (see {+@tbl:dbsrch}) is that the presented research must include sexual minority women as a focal population. For example, among the two empirical research articles returned from the fifth and sixth literature searches, which targeted SMW-inclusive IPV intervention and prevention research (see {+@tbl:dbsrch}), one examined male and female college students' perceptions of the prevalence of IPV perpetration among their peers [@witte2015perceived], and the other detailed an item-response theory approach to measuring teens' attitudes about dating violence among heterosexual adolescents [@edelen2009measurement]. While both of these studies somewhat reflect research aligned with community psychological values and methods, their substantive foci failed to meet this review's inclusion criteria for articles returned from the three database searches specific to sexual minority women.

Any articles not meeting the above-described three levels of inclusion criteria were excluded from remainder of analyses conducted for this review. This initial assessment and filtering analytic phase yeilded a final set of `r nrow(MAP)` empirical studies included in the below-described analyses and later-provided synthesis and methodological critique. Among these studies, `r nrow(MAP[MAP$scat == "S3", ])` are exclusively focused on or applicable only to heterosexual, and typically male-identified, poplations; whereas `r nrow(MAP[MAP$scat == "S4", ])` studies are specifically inclusive of female-identified lesbian, gay, bisexual, transgender, and/or queer groups and individuals (i.e., sexual minority women ["SMW"]).

```{r jcpkable}

jlvls <- levels(MAP$journal)
jncp <- j.cppr[!levels(factor(j.cppr)) %in% jlvls]

levels(MAP$journal) <- c(jlvls, jncp)

jcpv <- Rtdf(MAP$journal, names = c("j", "frq"))

jcpv$cpv <- ifelse(jcpv$j %in% j.cppr, "Community Psychology", "Violence")

jv <- jcpv[jcpv$cpv == "Violence", c("j", "frq")]

jcp <- jcpv[jcpv$cpv != "Violence", c("j", "frq")]


kable(jcp, col.names = c("Publication Title", "$N_{articles}$"), caption = "_Community-Psychology_-Specific Journal Titles Included in Literature Database Searches with the Corresponding Number of Formally Reviewed Articles per Journal {#tbl:jcp}")
```

```{r jvkable}
kable(jv, col.names = c("Publication Title", "$N_{articles}$"), caption = "_Violence_-Specific Journal Titles Included in Literature Database Searches with the Corresponding Number of Formally Reviewed Articles per Journal Included {#tbl:jv}")
```


## Synthesis & Methodological Evaluation

The second phase of deductive analysis served to examine the similarities, differences, and anomalies among the set of included articles according to the above-described two categories determined in the previous data reduction and organization process. Following a qualitative comparative analytic (QCA) approach [@leech2007array; @onwuegbuzie2017framework; @onwuegbuzie2009qualitative], I first reviewed each article in its entirety using a literature description and data extraction form (<a href="https://eccriley.github.io/CommPsy-SysLitRvw/attachments/TEMPLATE-LitDesc.pdf" target="_blank">available here</a>) that I created for this project. I developed this form with specific guidance from the systematic literature review and data extraction standards, protocols, templates, and guidelines provided by _The PRIMSA Group_ [@moher2009preferred] and the _Cochrane Collaboration's_ resources library and handbook for systematic reviews and meta-analyses [@higgins2011cochrane]. The literature description form consists of sections for recording each reviewed study's substantive research topic(s) (determined by the stated purpose(s), research question(s), and/or hypotheses, as provided in each article), target population(s)), target population(s), sampling frame setting(s), sampling frame(s), sampling methods, research design (e.g., experimental, cross-sectional, descriptive, etc.), overarching methodology (i.e., qualitative, quantitative, or mixed-methods), specific data collection methods (e.g., measures, interview questions, archival data sources, etc.), data analytic approaches and procedures, and key findings. The final piece of information included in the form is the ecological levels of analysis involved in a study's design, methods, and analysis. The ecological levels of analysis section was intentionally placed at the end of the description form so that the author could determine which levels of analysis were involved in each study based on the characteristics of the full array of information and study characteristics recorded in the prior sections of the form. That is, the ecological levels of analysis involved in each of the reviewed studies were inferred based on the other data points recorded in the literature description form for each reviewed study, all of which were directly extracted from the information provided in each article. The summative data across the reviewed studies were then compiled and restructured to form a methodologically-focused codebook, presented in {+@tbl:cdbk}, consisting of (1) _information categories_ corresponding to the research design and methods-related sections covered in the literature description form, and (2) the _codes_ generated in each information category from the discrete characteristics recorded in the description form across the reviewed studies.

`r tufte::newthought("Methodological Review \\& Evaluation")`

Research conducted within the subset of community psychology focused around intimate partner violence was initially evaluated according to the level of inclusion and exclusion of the historically marginalized population of particular interest for the purposes of this review: sexual minority women (SMW). The implementation of action-oriented community-psychology methodologies and analytic approaches was then reviewed within each of these categories (i.e., inclusion or exclusion of SMW) in terms of (1) the appropriateness of the methods to the research question(s), (2) how the methods facilitated the inclusion or exclusion of sexual minority women, and (3) whether and how (where applicable) exclusion of sexual minority women is justified.

`r tufte::newthought("Defining and Evaluating Methodological Rigor")`

The notion of "scientific rigor" is particularly important in evaluating a set of applied social science research studies employing varying methodologies. This is because "rigor" is not necessarily clearly defined across methodologies, and some research philosophies do not consider certain methodologies as capable of achieving scientific rigor at all. For the purposes of this review, methodological rigor is broadly defined as the extent to which a given study employs research methods that best address the overarching research question(s) and/or hypothesis/hypotheses, and the quality of the implementation of those methods. This definition of methodological rigor therefore does not prioritize a particular method nor category of methods (e.g., quantitative over qualitative, mixed-methods over single-methods, etc.), but rather prioritizes the choice and implementation of methods employed to address a given study's purposes. In addition, this definition of methodological rigor allows for more specific and in-depth consideration of the limitations presented, and not presented, in each study's report.

Rigor in action-oriented community-based research methods was evaluated according to the choice, description, justification, appropriateness, and execution of each reviewed study's design (i.e., experimental or cross-sectional) and overarching methodology (i.e., quantitative, qualitative, or mixed-methods). Each of these aspects of the reviewed literature was identified in terms of each evaluated study's purpose, hypotheses, and/or research questions description, sampling frame definition, sampling and data collection methods, analytic approach(es), and description of findings and limitations. Because the underlying goals of this systematic review are motivated by the continued relative absence of sexual minority women in the larger body of IPV-related empirical research literature, especially in terms of IPV perpetrator interventions research, particular attention was given to the sampling frame definitions and sampling methods employed among the empirical studies reviewed here. That is, the evaluated research included in the present review was specifically evaluated in terms of how the methods facilitate the inclusion or exclusion of specific populations, particularly sexual minority women, and whether and how the exclusion of specific populations is justified in each empirical study's report.

In addition, to assess transparency and reproducibility of the research methods and findings, the overall presentation, dissemination mechanism(s), application, and accessibility of the research was noted where available or applicable. These latter assessments of research transparency and reproducibility also incorporated considerations regarding the incorporation of key and/or distal stakeholders' input. The accessibility of the research to primary and distal stakeholders would be reflected according to whether and how stakeholders are provided information about and access to reports of a given project's progress and findings. The role of stakeholder input in the evaluated community-psychology literature was noted in terms of the extent to which efforts made to ensure that _all available_ stakeholders' and informants' voices are considered throughout the research process, and that certain voices are not unjustifiably privileged over others. These considerations include evaluation of whether feedback is explicitly solicited, or at least accepted when offered, from key stakeholders and informants to the research, and whether such feedback is genuinely considered by the primary researchers of a given investigation.

```{r tblcdbk}
cdbk.ft$clab <- gsub("\\n", "", cdbk.ft$clab)
kable(cdbk.ft, col.names = c("\\textbf{Information Category}", "Codes"), caption = "Codebook Constructed from the Discrete Summative Data Compiled Across the Formally Reviewed Literature {#tbl:cdbk}", align = c("r", "l"))
```

<hr class="Bold" />

`r Rcite_r(file = "../../auxDocs/REFs.bib", footnote = FALSE)`

-----

# References

<div class="refs">
