# Appendix A: Tables

```{r setup, echo=FALSE, results='hide', message=FALSE, warning=FALSE, cache=FALSE, fig.show='none', fig.keep='none'}
knitr::opts_chunk$set(echo=FALSE, results = 'asis')
```

```{r mapJrnl}
Rtdf(MAP$journal, names = c("Publication Title", "$N_{Articles}$")) %>%
    pander(caption = "Publication Titles of Reviewed Articles, and Number of Articles per Publication Title in Each Research Category")

MAPp <- dplyr::rename(MAP, "Publication Title" = journal, "Research Category" = scat)
MAPp[, "Research Category"] <- factor(MAPp[, "Research Category"], labels = c("IPV Interventions Research", "SMW-Inclusive IPV Research"))
jsft <- ftable(MAPp[, "Publication Title"], MAPp[, "Research Category"]) %>% as.matrix()
jsft <- ifelse(jsft == 0, NA, jsft)
pander(jsft)

```

\newpage

```{r dbsrch}
dbsrch <- data.frame(n = c("1.", "2.", "3.", "4.", "5.", "6."),
                     srch = c("Intimate Partner Violence, Domestic Violence, or Partner Abuse - General",
                              "Intimate Partner Violence, Domestic Violence, or Partner Abuse Interventions",
                              "Intimate Partner Violence, Domestic Violence, or Partner Abuse Intervention Evaluations",
                              "Female Same-Sex/Same-Gender Domestic Violence, or Partner Abuse - General",
                              "Female Same-Sex/Same-Gender Domestic Violence, or Partner Abuse Interventions",
                              "Female Same-Sex/Same-Gender Domestic Violence, or Partner Abuse Intervention Evaluations"),
                     nres = c(paste0("$", comma(s1[1]), " - ", comma(s1[2]), "$"),
                              paste0("$", comma(s2[1]), " - ", comma(s2[2]), "$"),
                              paste0("$", comma(s3[1]), " - ", comma(s3[2]), "$"),
                              paste0("$", comma(s4[1]), " - ", comma(s4[2]), "$"),
                              paste0("$", comma(s5[1]), " - ", comma(s5[2]), "$"),
                              paste0("$", comma(s6[1]), " - ", comma(s6[2]), "$"))
                     )

## BELOW IS FOR .TEX/.PDF OUTPUT ##
dbsrch$srch <- paste0("\\footnotesize{\\textit{", dbsrch$srch, "}}")
dbsrch$n <- paste0("\\footnotesize{\\textit{", dbsrch$n, "}}")
dbsrch$nres <- paste0("\\footnotesize{\\textit{", dbsrch$nres, "}}")

## BELOW IS FOR .DOCX OUTPUT ##
# dbsrch$srch <- paste0("_", dbsrch$srch, "_")
# dbsrch$n <- paste0("_", dbsrch$n, "_")
# dbsrch$nres <- paste0("_", dbsrch$nres, "_")

names(dbsrch) <- c("", "Database Search", "$Range_{N_{Results}}$")
kable(dbsrch, caption = "Descriptions of database searches conducted with corresponding ranges of the number of results returned", align = c("r", "l", "c"))

```


\newpage

# Appendix B: Qualitative Comparative Analysis Results

The tables and figures provided in this appendix represent the qualitative comparative analytic process and corresponding findings for the present review.

```{r echo=FALSE}
Rcite_r <-
    function(file = NULL,
             prefix = "R-",
             tex = FALSE,
             footnote = TRUE,
             ...) {
        if (!is.null(file))
            r_version <- as.character(packageVersion("base"))
        cite_just_r <-
            paste0("**R** [**v** ", r_version, ", @", prefix, "base]")
        if (is.null(file) || !file_test("-f", file)) {
            if (!is.null(file) || pkgs != "all")
                warning(
                    "File ",
                    file,
                    " not found. Cannot cite R-packages. If knitting again does not solve the problem, please check file path."
                )
            return(cite_just_r)
        }
        Rsearch <- function() {
            s <- search()
            s <- gsub("package:", "", s)
            return(s)
        }
        pkgs <- Riley::Rsearch()
        r_bib <- readLines(file)
        cite_keys <-
            r_bib[grepl(paste0("\\@\\w+\\{", prefix), r_bib)]
        cite_keys <- gsub("\\@\\w+\\{", "", cite_keys)
        cite_keys <- gsub("\\,", "", cite_keys)
        bib <- sapply(cite_keys, function(x) {
            y <- list(x)
            names(y) <- gsub(prefix, "", x)
            y
        }, USE.NAMES = FALSE)
        if (length(pkgs) > 1 && pkgs != "all") {
            pkg_citations <- bib[names(bib) %in% pkgs]
        }
        else {
            pkg_citations <- bib[!names(bib) == "base"]
        }
        if (length(pkg_citations) == 0) {
            return(cite_just_r)
        }
        vers1 <-
            function(x)
                as.data.frame(strsplit(as.character(packageVersion(x)), split = "\\."))[1,]
        vers2 <-
            function(x)
                as.data.frame(strsplit(as.character(packageVersion(x)), split = "\\."))[2,]
        pkg_texts <- paste0(
            "_",
            names(pkg_citations),
            "-v",
            sapply(names(pkg_citations), vers1),
            ".",
            sapply(names(pkg_citations), vers2),
            "._ ",
            "[@",
            unlist(pkg_citations),
            "]"
        )
        if (length(pkg_texts) > 1) {
            pkg_info <- paste(pkg_texts[1:(length(pkg_texts) - 1)],
                              collapse = ", ")
            pkg_info <- paste0(pkg_info, ", and ", tail(pkg_texts,
                                                        1))
        }
        else {
            pkg_info <- pkg_texts
        }
        if (footnote) {
            res <-
                paste0(
                    "^[**Note:** This process was conducted using the _**R**-v",
                    r_version,
                    "_ [@",
                    bib$base,
                    "], and the following _**R**-packages_:",
                    " ",
                    pkg_info,
                    "]"
                )
        }
        else {
            if (tex) {
                res <-
                    paste0(
                        "\n",
                        newthought("This document was created using "),
                        "_**R**-v",
                        r_version,
                        "_ [@",
                        bib$base,
                        "], and the following _**R**-packages_:",
                        "\n\n\\medskip\n\n",
                        pkg_info
                    )
            }
            else {
                res <-
                    paste0(
                        "\nThis process was conducted using the _R Statistical Programming Language and Environment_ [",
                        r_version,
                        "; @", bib$base, "], and the following _**R**-packages_: ",
                        "\n\n",
                        pkg_info
                    )
            }
        }
        return(res)
    }
#'
```

`r Rcite_r(file = "../auxDocs/REFs.bib", footnote = FALSE)`

```{r setup2, echo=FALSE, results='hide', message=FALSE, warning=FALSE, cache=FALSE}
# SETUP --------------------------------------------------------------

source("../SETUP.R")
knitr::opts_chunk$set(
    tidy = TRUE,
    echo = FALSE,
    fig.keep = 'high',
    fig.show = 'asis',
    results = 'asis',
    tidy.opts = list(comment = FALSE),
    echoRule = NULL,
    echoRuleb = NULL,
    fig.height = 5,
    fig.path = "graphics/bibs_cp/rplot-", dev = 'pdf')
# fig.retina = 4
rpm()
```


\Frule

\newpage

```{r journals}
# JOURNALS -----------------------------------------------------------
jdat <- read.csv("data/ipvJournalsSearch.csv")[c(-1, -6, -7), ]
## Exclude Theses and Dissertations ##

m.cnt <- mean(jdat[, 2])
s.cnt <- sd(jdat[, 2])
jdat$j <- as.integer(jdat$journal)

jv.sum <- sum(jdat$count)
jdat$prop <- jdat$count/jv.sum
jfv.n <- jdat[jdat$j == 59, 2]
jiv.n <- jdat[jdat$j == 61, 2]
vaw.n <- jdat[jdat$j == 94, 2]
jvv.n <- jdat[jdat$j == 96, 2]
jv.n <- rbind(jiv.n, jfv.n, vaw.n, jvv.n)

jdat.m <- jdat[jdat[,2] >= m.cnt, ]
jdat.s <- jdat[jdat[,2] >= s.cnt, ]

j.vpr <-c("Journal of Interpersonal Violence",
          "Violence Against Women",
          "Violence and Victims",
          "Journal of Family Violence")

j.v <- sapply(j.vpr, tolower, USE.NAMES = FALSE)

j.cppr <- c("Action Research",
            "American Journal of Community Psychology",
            "American Journal of Health Promotion",
            "American Journal of Orthopsychiatry",
            "American Journal of Preventive Medicine",
            "American Journal of Public Health",
            "Australian Community Psychologist",
            "Community Development",
            "Community Development Journal",
            "Community Mental Health Journal",
            "Community Psychology in Global Perspective",
            "Cultural Diversity and Ethnic Minority Psychology",
            "Global Journal of Community Psychology Practice",
            "Health Education and Behavior",
            "Health Promotion Practice",
            "Journal of Applied Social Psychology",
            "Journal of Community and Applied Social Psychology",
            "Journal of Community Practice",
            "Journal of Community Psychology",
            "Journal of Health and Social Behavior",
            "Journal of Prevention and Intervention",
            "Journal of Primary Prevention",
            "Journal of Rural Community Psychology",
            "Journal of Social Issues",
            "Journal of Community Psychology",
            "Psychiatric Rehabilitation Journal",
            "Psychology of Women Quarterly",
            "Social Science and Medicine",
            "The Community Psychologist",
            "Transcultural Psychiatry",
            "Progress in Community Health Partnerships")

j.cp <- sapply(j.cppr, tolower, USE.NAMES = FALSE)
```




```{r pander_journals, echo=FALSE}

### FUN - 'RtCap()' ####
RtCap <- function(x) {
    s0 <- strsplit(x, " ")[[1]]
    nocap <- c("a", "the", "to", "at", "in", "with", "and", "but", "or", "of")
    s1 <- ifelse(!s0 %in% nocap, toupper(substring(s0, 1,1)), s0)
    # s2 <- toupper(substring(s[!s %in% nocap], 1,1))
    s2 <- ifelse(!s0 %in% nocap, substring(s0, 2), "")
    s <- paste(s1, s2, sep="", collapse=" ")
    return(s)
}

j.cpp <- sapply(j.cp, RtCap, USE.NAMES = FALSE)
# cat(tufte::newthought("Community-psychology journals"), "included in database searches:\n\n")
# j.cpp %>% as.list() %>% pander()
```


\newpage

```{r bibdf}
### FUN - 'Rbibkeys()' ####
Rbibkeys <- function(bib) {
    keys <- bib[grep("\\@.*?\\{.*?,", bib, perl = TRUE)]
    keys <- gsub("\\@\\w+\\{(.*?)", "\\1", keys, perl = TRUE)
    keys <- keys[!grepl("\\%.*?,", keys, perl = TRUE)]
    keys <- gsub(" ", NA_character_, keys)
    keys <- gsub(",", "", keys)
    return(keys)
}

# BIB --------------------------------------------------------------

bib <- readLines("MAP.bib")
BIBKEY <- Rbibkeys(bib)

library(bib2df)
bibdf <- bib2df("MAP.bib")

### n.init ####
n.init <- nrow(bibdf)

ID <- seq(1:nrow(bibdf))
MAP.au <- cbind(BIBKEY, bibdf[, "AUTHOR"])
## bibdf[,2] ##
```



```{r MAP}
# MAP ----------------------------------------------------------------
MAP <- cbind(ID,
             BIBKEY,
             bibdf[, c("YEAR", "TITLE", "JOURNAL", "ABSTRACT")]) %>%
    as.data.frame()
## bibdf[c(3:5, 8)] ##
names(MAP)[-1] <- tolower(names(MAP)[-1])
```



```{r MAP_RQDA, results='hide', fig.keep='none', fig.show='none'}
# MAP-RQDA ----------------------------------------------------------------
source("MAPrqda.R", echo = FALSE)
```



```{r }
csid <- caseids[, c("caseid", "case", "RM", "scat")]
## caseids[, -3] ##
csid$case <- factor(csid$case)

MAP <- merge(MAP, csid, by.x = "bibkey", by.y = "case")
```


```{r MAP_CPV}

# MAP-CPV ----------------------------------------------------------------

## (map.cp & map.v) ============================================================

MAP$journal <- sapply(MAP$journal, tolower)
MAP$journal <- gsub(" & ", " and ", MAP$journal)
MAP$journal <- factor(MAP$journal)

cp <- MAP$journal %in% j.cp
map.cp <- MAP[cp, , drop = FALSE]
levels(map.cp$journal) <- c(levels(map.cp$journal),
                            j.cp[!j.cp %in% levels(map.cp$journal)])
levels(map.cp$journal) <- sapply(levels(map.cp$journal), RtCap)

MAP <- map.cp
```

```{r }
MAP$RM <- ifelse(MAP$RM == 1, NA_character_, 0)
MAPrm <- MAP[is.na(MAP$RM), "bibkey"] %>% droplevels() %>% as.character()
MAP <- na.omit(MAP)
MAP <- droplevels(MAP)
```

```{r }
## map-jrnl ============================================================
MAP$journal <- factor(MAP$journal)
levels(MAP$journal) <- sapply(levels(MAP$journal), RtCap)
MAP$journal <- droplevels(MAP$journal)

### FUN - 'Rabbr()' ####
Rabbr <- function(x) {
    s0 <- strsplit(x, " ")[[1]]
    ex <- c("a", "the", "to", "at", "in", "with", "and", "but", "or", "of", "\\&")
    s1 <- s0[!s0 %in% ex]
    s2 <- substring(s1, 1,1)
    s <- paste(s2, sep = "", collapse = "")
    s <- toupper(s)
    return(s)
}

MAP$jrnl <- sapply(as.character(MAP$journal), Rabbr)
```


\newpage

# \textsc{Systematically-Reviewed Literature}

\Frule

```{r cb}

# CTBL ---------------------------------------------------------------

cb <- merge(MAP, ctbl, by = c("caseid", "scat"))
cb <- within(cb, {
    journal <- droplevels(journal)
    jrnl <- sapply(as.character(journal), Rabbr)
    code <- gsub("FG-\\w+", "FG", code)
    # code <- gsub("EXP-\\w+", "EXP", code)
    # code <- gsub("LT-\\w+", "LT", code)
    code <- gsub("SVY-QL-MM", "SVY-QL", code)
    code <- gsub("SVY-QT-MM", "SVY-QT", code)
    # code <- gsub("XS-\\w+", "XS", code)
    code <- gsub("IVW-\\w+", "IVW", code)
    code <- gsub("SMIN-\\w+", NA, code)
    code <- gsub("HET", NA, code)
    scat <- factor(scat, labels = c("IPV Interventions", "SMW-Inclusive Research"))
})
cb <- na.omit(cb) %>% droplevels()

# cbk$clab <- ifelse(cbk$code %in% cb$code, cbk$clab, NA)
# cbk <- na.omit(cbk) %>% droplevels()

cb <- merge(cb, cbk, by = "code")
cb$code <- factor(cb$code)
cb$clab <- factor(cb$clab)
```

## General Research Categories


```{r desc}
### catpal ####

catpal <- c(adjustcolor(pal_my[16], alpha.f = 0.9), adjustcolor(pal_my[5], alpha.f = 0.9))

# DESCRIPTIVES ---------------------------------------------------------------

## search categories ============================================================

### [MAP-abstracts-S3.csv] ####
cpv.s3 <- MAP[MAP$scat == "S3", ]; ## write.csv(cpv.s3[order(cpv.s3$year), c("bibkey", "year", "title", "journal", "abstract")], "data/MAP-abstracts-S3.csv", row.names = FALSE)

### [MAP-abstracts-S4.csv] ####
cpv.s4 <- MAP[MAP$scat == "S4", ]; ## write.csv(cpv.s4[order(cpv.s4$year), c("bibkey", "year", "title", "journal", "abstract")], "data/MAP-abstracts-S4.csv", row.names = FALSE)

ct.scat <- within(MAP, {
    scat <- ifelse(scat == "S3", "IPV Interventions", "SMW-Inclusive Research")
})

t.scat <- Rtdf(ct.scat$scat, names = c("Category", "N"))
## "ct.scat" created in "MAPrqda.R" ##
t.scat %>% kable()
scat.t <- table(ct.scat$scat)
scat.bn <- Rbinom(scat.t)
scat.bn %>% pander(caption = "Binomial Test of the Difference in Search Category Proportions")

t.scat$prop = t.scat$N / sum(t.scat$N)
t.scat <- t.scat[order(t.scat$prop), ]
t.scat$ymax <- cumsum(t.scat$prop)
t.scat$ymin <- c(0, head(t.scat$ymax, n = -1))

### PLOT - scat ####
library(ggplot2)
scat.p <- ggplot(t.scat, aes(fill = Category,
                             ymax = ymax,
                             ymin = ymin,
                             xmax = 4,
                             xmin = 3)) +
    scale_fill_manual(values = catpal) +
    geom_rect() +
    coord_polar(theta = "y") +
    xlim(c(0, 4)) +
    annotate("text", x = 0, y = 0, label = "Category Proportions") +
    labs(title = "") +
    thm_Rtft(ytitle = FALSE) +
    theme(axis.text = element_blank(),
          axis.ticks = element_blank(),
          legend.text = element_text(size = rel(1)),
          legend.key.width = unit(0.5, "cm"),
          legend.key.height = unit(0.5, "cm"))
scat.p
```



\newpage

## Publication Titles
\Frule


```{r pub_titles}
## publication titles ============================================================
t.jrnl <- Rtdf(MAP$journal)
ft.jrnl <- with(MAP, {
    ftable(journal, scat) %>%
        matrix(nrow = nrow(t.jrnl),
               byrow = FALSE)
})
dimnames(ft.jrnl) <- list("Publication Title" = levels(MAP$journal),
                          Category = c("IPV Interventions", "SMW-Inclusive Research"))
ft.jrnl <- ifelse(ft.jrnl == 0, NA, ft.jrnl)
ft.jrnl %>% pander(caption = "Number of Publications in Each Research Category per Journal",
                   justify = c("left", "right", "right"))

cpv.s3$jrnl <- sapply(as.character(cpv.s3$journal), Rabbr) %>% factor()
cpv.s4$jrnl <- sapply(as.character(cpv.s4$journal), Rabbr) %>% factor()
j.cp <- sapply(j.cp, Rabbr, USE.NAMES = FALSE)
```

## Research Category by Journal & Journal Category


```{r scat_x_journal}
ftm.j <- Rna(ft.jrnl)
sum.j <- apply(ftm.j, 1, sum)
ftm.jp <- cbind(ft.jrnl, "**Total**" = sum.j)
ftm.jp %>% pander(justify = c("left", "right", "right", "right"),
                  caption = "$N_{articles}$ in Each Research Category per Journal")

Rdotchart(
    ftm.j,
    pch = 19,
    gcolor = pal_my[20],
    xlab = expression(N[Articles]),
    cex = 0.7,
    gcex = 0.75,
    gfont = 2,
    pt.cex = 1.125,
    color = c(rep(catpal[1], nrow(ftm.j)), rep(catpal[2], nrow(ftm.j))),
    xaxt = 'n'
); axis(1, at = seq(range(ftm.j, na.rm = TRUE)[1],
                    range(ftm.j, na.rm = TRUE)[2], by = 3))

MAP.j <- MAP[, c("scat", "journal")]
names(MAP.j) <- c("Category", "Journal")
MAP.j$Category <- ifelse(MAP.j$Category == "S3",
                         "IPV Interventions",
                         "SMW-Inclusive Research")
pj <- mpal(1:length(unique(MAP$jrnl)), p = sci)
library(ggparallel)
pscat <- c("#a6afbb", pal_my[17])

j.ps <- ggparset2(list("Category", "Journal"),
                  data = MAP.j,
                  method = "parset", label = TRUE,
                  label.size = 2.75, text.angle = 0, order = c(1, 1)) +
    scale_fill_manual(values = c(pscat, adjustcolor(pj, alpha.f = 0.55)),
                      guide = FALSE) +
    scale_colour_manual(values = c(pscat, pj), guide = FALSE) +
    thm_Rtft(ticks = FALSE, ytext = FALSE)
j.ps
```

\newpage

## Research Topics, Sampling Frames, and Methodologies



```{r FUN_Rftm}

### FUN - 'Rftm()' ####

Rftm <- function(x1, x2, dnn = NULL, zero.action = NA, zero.qt = FALSE) {
    if (!is.null(dnn)) {
        tx <- Rtdf(x1, names = dnn[[1]])
        ftm <- ftable(x1, x2, row.vars = 1) %>%
            matrix(nrow = nrow(tx), byrow = FALSE)
        dimnames(ftm) <- list(levels(x1), dnn[[2]])
    } else {
        tx <- Rtdf(x1)
        ftm <- ftable(x1, x2, row.vars = 1) %>%
            matrix(nrow = nrow(tx), byrow = FALSE)
        dimnames(ftm) <- list(levels(x1))
    }
    if (!is.null(zero.action)) {
        if (zero.qt == 0 | zero.qt == 1) {
            zero.qt <- as.logical(zero.qt)
        }
        if (zero.qt == TRUE) {
            ftm <- ifelse(ftm == 0, quote(zero.action), ftm)
        } else {
            ftm <- ifelse(ftm == 0, noquote(zero.action), ftm)
        }
    }
    y <- list(tx, ftm)
    names(y) <- c(paste0("Tabulation of ", deparse(substitute(x1))),
                  paste0("Cross-Tabulation of ",
                         deparse(substitute(x1)),
                         " & ",
                         deparse(substitute(x2))))
    return(y)
}
```


\Frule

`r tufte::newthought("\\Large{Primary Topics}")`


```{r topics, fig.fullwidth=TRUE, fig.height = 7.5}

## topics ============================================================
# cb$clab <- factor(cb$clab)
codes.tp <- cb[cb$cat == "TOPIC", "clab"] %>% droplevels()
ctp.dnn <- c("Topic", "$N_{Articles}$")
scats.tp <- cb[cb$cat == "TOPIC", "scat"] %>% droplevels()
stp.dnn <- c("IPV Interventions", "SMW-Inclusive Research")
topics <- Rftm(codes.tp, scats.tp, dnn = list(ctp.dnn, stp.dnn))
t.tp <- topics[[1]]
ftm.tp <- topics[[2]]
ftm.tp2 <- Rna(ftm.tp)
sum.tp <- apply(ftm.tp2, 1, sum)
ftm.tpp <- cbind(ftm.tp, "**Total**" = sum.tp)
ftm.tpp %>% pander(justify = c("left", "right", "right", "right"),
                   caption = "Research Topics")

### PLOT - topic - 1 ####
Rdotchart(
    ftm.tp,
    pch = 19,
    gcolor = pal_my[20],
    xlab = expression(N[Articles]),
    cex = 0.7,
    gcex = 0.75,
    gfont = 2,
    pt.cex = 1.125,
    color = c(rep(catpal[1], nrow(ftm.tp)), rep(catpal[2], nrow(ftm.tp))))
## xaxt = 'n'
#; axis(1, at = seq(range(ftm.tp, na.rm = TRUE)[1],
## range(ftm.tp, na.rm = TRUE)[2], by = 3))
```


\newpage


```{r topics2, fig.fullwidth=TRUE}
dfm.tp2 <- data.frame(ftm.tp)
names(dfm.tp2) <- c("s3", "s4")
top.s3 <- data.frame(dfm.tp2$s3, row.names = rownames(dfm.tp2))
top.s3 <- na.omit(top.s3)
# top.s3
top.s4 <- data.frame(dfm.tp2$s4, row.names = rownames(dfm.tp2))
top.s4 <- na.omit(top.s4)
# top.s4

tp.s3 <- cb[cb$scat == levels(cb$scat)[1] &
                cb$cat == "TOPIC", ] %>%
    droplevels()
tp.s4 <- cb[cb$scat == levels(cb$scat)[2] &
                cb$cat == "TOPIC", ] %>%
    droplevels()
```


\newpage

`r tufte::newthought("\\Large{Research Designs}")`


```{r designs, fig.fullwidth=TRUE}
## designs ============================================================

ct.d <- cb[cb$cat == "DESIGN", ] %>% droplevels()
t.d <- Rtdf(ct.d$clab)
ct.d$clab <- gsub(" Design", "", ct.d$clab) %>% factor()
ft.d <- ftable(ct.d[, c("clab", "scat")], row.vars = 1)
ftm.d <- matrix(ft.d, nrow = nrow(t.d), byrow = FALSE)
dimnames(ftm.d) <- list(Design = levels(ct.d$clab),
                        Category = c("IPV Interventions",
                                     "SMW-Inclusive Research"))
sum.d <- apply(ftm.d, 1, sum)
ftm.d <- ifelse(ftm.d == 0, NA, ftm.d)
ftm.d <- cbind(ftm.d, "**Total**" = sum.d)
ftm.d %>% pander(justify = c("left", "right", "right", "right"),
                 caption = "Overarching Research Designs")

nlabs <- length(unique(ct.d$clab))
pmo <- mpal(1:length(unique(ct.d$clab)), p = sci)

ct.d <- dplyr::rename(ct.d, "Category" = scat, "Design" = clab)

### PLOT - designs ####

library(ggparallel)
pscat <- c("#a6afbb", pal_my[17])
d.ps <- ggparset2(list("Category", "Design"),
                  data = ct.d,
                  method = "parset", label = TRUE,
                  label.size = 3.5, text.angle = 0, order = c(1, 1)) +
    scale_fill_manual(values = c(pscat, adjustcolor(pmo, alpha.f = 0.55)),
                      guide = FALSE) +
    scale_colour_manual(values = c(pscat, pmo), guide = FALSE) +
    thm_Rtft(ticks = FALSE, ytext = FALSE)
d.ps
```


\newpage

`r tufte::newthought("\\large{Experimental Research Designs}")`


```{r exp, fig.fullwidth=TRUE}
## experimental designs ============================================================

ct.exp <- cb[cb$cat == "DESIGN-EXP", ] %>% droplevels()
t.exp <- Rtdf(ct.exp$clab)
ct.exp$clab <- gsub(" Design", "", ct.exp$clab) %>% factor()
ct.exp$clab <- gsub(" \\(", " \n\\(", ct.exp$clab) %>% factor()
ft.exp <- ftable(ct.exp[, c("clab", "scat")], row.vars = 1)
ftm.exp <- matrix(ft.exp, nrow = nrow(t.exp), byrow = FALSE)
dimnames(ftm.exp) <- list("Experimental Design" = levels(ct.exp$clab),
                          Category = c("IPV Interventions",
                                       "SMW-Inclusive Research"))
sum.exp <- apply(ftm.exp, 1, sum)
ftm.exp <- ifelse(ftm.exp == 0, NA, ftm.exp)
ftm.exp <- cbind(ftm.exp, "**Total**" = sum.exp)
ftm.exp %>% pander(justify = c("left", "right", "right", "right"),
                   caption = "Experimental Research Designs")

nlabs <- length(unique(ct.exp$clab))
pmo <- mpal(1:length(unique(ct.exp$clab)), p = sci)

ct.exp <- dplyr::rename(ct.exp, "Category" = scat, "Experimental Design" = clab)

### PLOT - experimental designs ####

library(ggparallel)
pscat <- c("#a6afbb", pal_my[17])
exp.ps <- ggparset2(list("Category", "Experimental Design"),
                    data = ct.exp,
                    method = "parset", label = TRUE,
                    label.size = 3, text.angle = 0, order = c(1, 1)) +
    scale_fill_manual(values = c(pscat, adjustcolor(pmo, alpha.f = 0.55)),
                      guide = FALSE) +
    scale_colour_manual(values = c(pscat, pmo), guide = FALSE) +
    thm_Rtft(ticks = FALSE, ytext = FALSE)
exp.ps
```


\newpage
`r tufte::newthought("\\Large{Data Collection Methodologies}")`


```{r methodologies, fig.fullwidth=TRUE}
## methodologies ============================================================

### PLOT - methodologies - 1 ####

ct.mo <- cb[cb$cat == "METHODS", ] %>% droplevels()
t.mo <- Rtdf(ct.mo$clab)

ft.mo <- ftable(ct.mo[, c("clab", "scat")], row.vars = 1)
ftm.mo <- matrix(ft.mo, nrow = nrow(t.mo), byrow = FALSE)
dimnames(ftm.mo) <- list(Methodology = levels(ct.mo$clab),
                         Category = c("IPV Interventions",
                                      "SMW-Inclusive Research"))
sum.mo <- apply(ftm.mo, 1, sum)
ftm.mo <- ifelse(ftm.mo == 0, NA, ftm.mo)
ftm.mo <- cbind(ftm.mo, "**Total**" = sum.mo)
ftm.mo %>% pander(justify = c("left", "right", "right", "right"),
                  caption = "Methodologies")

### PLOT - methodologies ####

nlabs <- length(unique(ct.mo$clab))
pmo <- mpal(1:length(unique(ct.mo$clab)), p = sci)

ct.mo <- dplyr::rename(ct.mo, "Category" = scat, "Methodology" = clab)

library(ggparallel)
pscat <- c("#a6afbb", pal_my[17])
mo.ps <- ggparset2(list("Category", "Methodology"),
                   data = ct.mo,
                   method = "parset", label = TRUE,
                   label.size = 3.5, text.angle = 0, order = c(1, 1)) +
    scale_fill_manual(values = c(pscat, adjustcolor(pmo, alpha.f = 0.55)),
                      guide = FALSE) +
    scale_colour_manual(values = c(pscat, pmo), guide = FALSE) +
    thm_Rtft(ticks = FALSE, ytext = FALSE)
mo.ps
```


\newpage
`r tufte::newthought("\\large{QuaLitative \\textit{Methods}}")`


```{r qual, fig.fullwidth=TRUE}
## qualitative ============================================================

ct.ql <- cb[cb$cat == "M-QL", ] %>% droplevels()
t.ql <- Rtdf(ct.ql$clab)
ft.ql <- ftable(ct.ql[, c("clab", "scat")], row.vars = 1)
ftm.ql <- matrix(ft.ql, nrow = nrow(t.ql), byrow = FALSE)
dimnames(ftm.ql) <- list("Qua**L**itative Method(s)" = levels(ct.ql$clab),
                         Category = c(#"IPV Interventions",
                                      "SMW-Inclusive Research"))
sum.ql <- apply(ftm.ql, 1, sum)
ftm.ql <- ifelse(ftm.ql == 0, NA, ftm.ql)
ftm.ql <- cbind(ftm.ql, "**Total**" = sum.ql)
ftm.ql %>% pander(justify = c("left", "right", "right"),
                  caption = "Qua**L**itative Method(s)")

### PLOT - qualitative ####
pql <- mpal(1:length(unique(ct.ql$clab)), p = sci)

ct.ql <- dplyr::rename(ct.ql, "QuaLitative Methods" = clab, "Category" = scat)


ql.ps <- ggparset2(list("Category", "QuaLitative Methods"),
                   data = na.omit(ct.ql),
                   method = "parset", label = TRUE,
                   label.size = 3.5, text.angle = 0, order = c(1, 1)) +
    scale_fill_manual(values = c(pscat[1], adjustcolor(pql, alpha.f = 0.55)),
                      guide = FALSE) +
    scale_colour_manual(values = c(pscat[1], pql), guide = FALSE) +
    thm_Rtft(ticks = FALSE, ytext = FALSE)
ql.ps
```


\newpage

`r tufte::newthought("\\large{QuaNTitative Research \\textit{Designs}}")`


```{r quaNT_designs, fig.fullwidth=TRUE}
ct.dqt <- cb[cb$cat == "D-QT", ] %>% droplevels()
t.dqt <- Rtdf(ct.dqt$clab)
ft.dqt <- ftable(ct.dqt[, c("clab", "scat")], row.vars = 1)
ftm.dqt <- matrix(ft.dqt, nrow = nrow(t.dqt), byrow = FALSE)
dimnames(ftm.dqt) <- list("Qua**NT**itative Design" = levels(ct.dqt$clab),
                          Category = c("IPV Interventions",
                                       "SMW-Inclusive Research"))
# t.dqt
sum.dqt <- apply(ftm.dqt, 1, sum)
ftm.dqt <- ifelse(ftm.dqt == 0, NA, ftm.dqt)
ftm.dqt <- cbind(ftm.dqt, "**Total**" = sum.dqt)
ftm.dqt %>% pander(justify = c("left", "right", "right", "right"),
                   caption = "Qua**NT**itative Designs")

### PLOT - quantitative ####

nlabs <- length(unique(ct.dqt$clab))
pqt <- mpal(1:length(unique(ct.dqt$clab)), p = sci)

ct.dqt <- dplyr::rename(ct.dqt, "QuaNTitative Design" = clab, "Category" = scat)


dqt.ps <- ggparset2(list("Category", "QuaNTitative Design"),
                    data = ct.dqt,
                    method = "parset", label = TRUE,
                    label.size = 3.5, text.angle = 0, order = c(1, 1)) +
    scale_fill_manual(values = c(pscat, adjustcolor(pqt, alpha.f = 0.55)),
                      guide = FALSE) +
    scale_colour_manual(values = c(pscat, pqt), guide = FALSE) +
    thm_Rtft(ticks = FALSE, ytext = FALSE)
dqt.ps
```



\newpage
`r tufte::newthought("\\large{QuaNTitative \\textit{Methods}}")`


```{r quant, fig.fullwidth=TRUE, fig.height=6}
### quantitative ============================================================

ct.qt <- cb[cb$cat == "M-QT", ] %>% droplevels()
t.qt <- Rtdf(ct.qt$clab)
ft.qt <- ftable(ct.qt[, c("clab", "scat")], row.vars = 1)
ftm.qt <- matrix(ft.qt, nrow = nrow(t.qt), byrow = FALSE)
dimnames(ftm.qt) <- list("Qua**NT**itative Method" = levels(ct.qt$clab),
                         Category = c("IPV Interventions",
                                      "SMW-Inclusive Research"))
# t.qt
sum.qt <- apply(ftm.qt, 1, sum)
ftm.qt <- ifelse(ftm.qt == 0, NA, ftm.qt)
ftm.qt <- cbind(ftm.qt, "**Total**" = sum.qt)
ftm.qt %>% pander(justify = c("left", "right", "right", "right"),
                  caption = "Qua**NT**itative Methods")

### PLOT - quantitative ####

nlabs <- length(unique(ct.qt$clab))
pqt <- mpal(1:length(unique(ct.qt$clab)), p = sci)

ct.qt <- dplyr::rename(ct.qt, "QuaNTitative Methods" = clab, "Category" = scat)


qt.ps <- ggparset2(list("Category", "QuaNTitative Methods"),
                   data = ct.qt,
                   method = "parset", label = TRUE,
                   label.size = 3.5, text.angle = 0, order = c(1, 1)) +
    scale_fill_manual(values = c(pscat, adjustcolor(pqt, alpha.f = 0.55)),
                      guide = FALSE) +
    scale_colour_manual(values = c(pscat, pqt), guide = FALSE) +
    thm_Rtft(ticks = FALSE, ytext = FALSE)
qt.ps
```


\newpage

`r tufte::newthought("Archival/Secondary Data Sources")`


```{r m_rcrd, fig.fullwidth=TRUE}
### archival/secondary data sources ####
ct.rcrd <- cb[cb$cat == "M-RCRD", ] %>% droplevels()
t.rcrd <- Rtdf(ct.rcrd$clab)
ft.rcrd <- ftable(ct.rcrd[, c("clab", "scat")], row.vars = 1)
ftm.rcrd <- matrix(ft.rcrd, nrow = nrow(t.rcrd), byrow = FALSE)
dimnames(ftm.rcrd) <- list("Archival Data Source" = levels(ct.rcrd$clab),
                           Category = c(#"IPV Interventions",
                                        "SMW-Inclusive Research"))
# t.rcrd
sum.rcrd <- apply(ftm.rcrd, 1, sum)
ftm.rcrd <- ifelse(ftm.rcrd == 0, NA, ftm.rcrd)
ftm.rcrd <- cbind(ftm.rcrd, "**Total**" = sum.rcrd)
ftm.rcrd %>% pander(justify = c("left", "right", "right"),
                    caption = "Archival Data Sources")

### PLOT - archival/secondary data sources ####

nlabs <- length(unique(ct.rcrd$clab))
prcrd <- mpal(1:length(unique(ct.rcrd$clab)), p = sci)

ct.rcrd <- dplyr::rename(ct.rcrd, "Archival Data Source" = clab, "Category" = scat)


rcrd.ps <- ggparset2(list("Category", "Archival Data Source"),
                     data = ct.rcrd,
                     method = "parset", label = TRUE,
                     label.size = 3.5, text.angle = 0, order = c(1, 1)) +
    scale_fill_manual(values = rev(c(rev(pscat), adjustcolor(prcrd, alpha.f = 0.55))),
                      guide = FALSE) +
    scale_colour_manual(values = rev(c(rev(pscat), prcrd)), guide = FALSE) +
    thm_Rtft(ticks = FALSE, ytext = FALSE)
rcrd.ps
```


\newpage

`r tufte::newthought("\\large{Mixed-Methodological \\textit{Designs}}")`


```{r mm_designs, fig.fullwidth=TRUE}
## mixed-methods designs ========================================================

ct.dmm <- cb[cb$cat == "D-MM", ] %>% droplevels()
t.dmm <- Rtdf(ct.dmm$clab)
ft.dmm <- ftable(ct.dmm[, c("clab", "scat")], row.vars = 1)
ftm.dmm <- matrix(ft.dmm, nrow = nrow(t.dmm), byrow = FALSE)
dimnames(ftm.dmm) <- list("Mixed-Methodological Design" = levels(ct.dmm$clab),
                          scat = c(#"IPV Interventions",
                                   "SMW-Inclusive Research"))
# t.dmm
sum.dmm <- apply(ftm.dmm, 1, sum)
ftm.dmm <- ifelse(ftm.dmm == 0, NA, ftm.dmm)
ftm.dmm <- cbind(ftm.dmm, "**Total**" = sum.dmm)
ftm.dmm %>% pander(justify = c("left", "right", "right"),
                   caption = "Mixed-Methodological Designs")

### PLOT - mixed-methods ####

nlabs <- length(unique(ct.dmm$clab))
pmm <- mpal(1:length(unique(ct.dmm$clab)), p = sci)

ct.dmm <- dplyr::rename(ct.dmm, "Mixed-Methodological Design" = clab, "Category" = scat)


dmm.ps <- ggparset2(list("Category", "Mixed-Methodological Design"),
                    data = ct.dmm,
                    method = "parset", label = TRUE,
                    label.size = 3.5, text.angle = 0, order = c(-1,-1)) +
    scale_fill_manual(values = c(pscat, adjustcolor(pmm, alpha.f = 0.55)),
                      guide = FALSE) +
    scale_colour_manual(values = c(pscat, pmm), guide = FALSE) +
    thm_Rtft(ticks = FALSE, ytext = FALSE)
dmm.ps
```

\newpage

`r tufte::newthought("\\large{Mixed (QuaLitative \\& QuaNTitative) \\textit{Methods}}")`


```{r mm_methods, fig.fullwidth=TRUE}
## mixed-methods ============================================================

ct.mm <- cb[cb$cat == "M-MM", ] %>% droplevels()
t.mm <- Rtdf(ct.mm$clab)
ft.mm <- ftable(ct.mm[, c("clab", "scat")], row.vars = 1)
ftm.mm <- matrix(ft.mm, nrow = nrow(t.mm), byrow = FALSE)
dimnames(ftm.mm) <- list("Mixed-Methods" = levels(ct.mm$clab),
                         scat = c(#"IPV Interventions",
                                  "SMW-Inclusive Research"))
# t.mm
sum.mm <- apply(ftm.mm, 1, sum)
ftm.mm <- ifelse(ftm.mm == 0, NA, ftm.mm)
ftm.mm <- cbind(ftm.mm, "**Total**" = sum.mm)
ftm.mm %>% pander(justify = c("left", "right", "right"),
                  caption = "Research Topics")

### PLOT - mixed-methods ####

nlabs <- length(unique(ct.mm$clab))
pmm <- mpal(1:length(unique(ct.mm$clab)), p = sci)

ct.mm <- dplyr::rename(ct.mm, "Mixed-Methods" = clab, "Category" = scat)


mm.ps <- ggparset2(list("Category", "Mixed-Methods"),
                   data = na.omit(ct.mm),
                   method = "parset", label = TRUE,
                   label.size = 3.5, text.angle = 0, order = c(-1,-1)) +
    scale_fill_manual(values = c(pscat, adjustcolor(pmm, alpha.f = 0.55)),
                      guide = FALSE) +
    scale_colour_manual(values = c(pscat, pmm), guide = FALSE) +
    thm_Rtft(ticks = FALSE, ytext = FALSE)
mm.ps
```


\newpage

`r tufte::newthought("\\Large{Target Populations \\& Sampling Frames}")`


```{r populations, fig.fullwidth=TRUE, fig.height = 7.5}
## populations ============================================================

ct.pop <- cb[cb$cat == "POPULATION", ] %>% droplevels()
t.pop <- Rtdf(ct.pop$clab)
ft.pop <- ftable(ct.pop[, c("clab", "scat")], row.vars = 1)
ftm.pop <- matrix(ft.pop, nrow = nrow(t.pop), byrow = FALSE)
dimnames(ftm.pop) <-
    list(
        "Populations" = levels(ct.pop$clab),
        scat = c("IPV Interventions", "SMW-Inclusive Research")
    )

sum.pop <- apply(ftm.pop, 1, sum)
ftm.pop <- ifelse(ftm.pop == 0, NA, ftm.pop)
ftm.popp <- cbind(ftm.pop, "**Total**" = sum.pop)
ftm.popp %>% pander(justify = c("left", "right", "right", "right"),
                    caption = "Research Topics")

### PLOT - populations - 1 ####

Rdotchart(
    ftm.pop,
    pch = 19,
    gcolor = pal_my[20],
    xlab = expression(N[Articles]),
    cex = 0.7,
    gcex = 0.75,
    gfont = 2,
    pt.cex = 1.125,
    color = c(rep(catpal[1], nrow(ftm.pop)), rep(catpal[2], nrow(ftm.pop))))
```


\newpage

# Appendix C Clinician Rating Form [@gondolf2009clinician]

\setlength{\parindent}{0in}

Date:

Subject Name:

Group Leader (initials): Site:

INSTRUCTIONS: Please rate the man named above on each of the listed criteria. Rate him using the 0 to 5 scale below based on your impressions and observations. Return the form immediately to the evaluation contact person. 5 = extremely present; 4 = very present; 3 = somewhat present; 2 = a little present; 1 = very little present; 0 = no opinion, uncertain, not applicable.

_____ attendance: arrives at group session on time; socializes or lingers afterward; contacts program in advance about absence; has legitimate excuse for absences.
_____ nonviolence: has not recently physically abused partner, children, or others; no apparent threats, intimidation, or manipulation.
_____ sobriety: attends meeting sober; not high or drunk; no apparent abuse of alcohol or drugs during week; complying to ordered or referred drug and alcohol treatment.
_____ acceptance: admits that violence and abuse exists; not minimizing, blaming, or excusing the problem; realizes responsibility for abuse; identifies contribution to problems
_____ using techniques: takes conscious steps to avoid violence; refers to time-outs, self-talk, conflict resolution skills, etc.; does homework assignments or recommendations.
_____ help seeking: seeks information about alternatives; discusses options with others in the group; calls other participants for help; open to referrals and future support.
_____ process conscious: lets others speak one at time; acknowledges others’ contributions; asks questions of others without interrogating; heeds direction of counselors.
_____ actively engaged: attentive body language and nonverbal response; maintains eye contact; speaks with feeling; follows topic of discussion in comments.
_____ self-disclosure: reveals struggles, feelings, fears, and self-doubts; not withholding or evading issues; not sarcastic or defensive.
_____ sensitive language: respectful of partner and women in general; nonsexist language and no pejorative slang; checks others who use sexist language.

\newpage

\parindent=-1.75em

# References


\parindent=-1.75em

\setlength{\parskip}{0.25\baselineskip}
